---
title: "Supplemental Method 17: Univariate Control Analysis"
output: html_notebook
---

Sam Audrain August 2022
V 2.0

Trialwise univariate activation was extracted from the mPFC (for trials where got context correct) and hippocampi (for trials where got context and scene correct). Here, we test for effects of congruency and delay on univariate activation.

# Load packages 
```{r}

library(lme4)
library(ggplot2)
library(emmeans)
library(MuMIn)
library(car)

```

# mPFC 

## Create dataset for stats comparisons

R/UR trialwise univariate, regardless of detail (used for mPFC)

```{r}


delays<-c("short", "long")

conds<-c("R", "UR")

masks<-c("BNA_mPFC2_funcspace_thr0.95")

#subjects in CB1 counterbalancing condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")

for (delay in delays){
  for (cond in conds){
    for (mask in masks){
       data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/extracted_betas_trialwise/",cond,"_act_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
       colnames(data)<- c("subj", "trial", "mask", "uni_act")
       # add conditions
       data$delay<-rep(delay, (nrow(data)))
       data$condition<-rep(cond, (nrow(data)))
       data$CB_order<-rep(2, nrow(data))
       # name participants consistently across sessions 
       for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
       # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        }
      }
       name<-paste(delay,mask,cond, sep="_")
       assign(name,data) #saves the mean and std under the current masks name
    }
  }
}

# create dataset 
mPFC_data<-rbind(short_BNA_mPFC2_funcspace_thr0.95_R, short_BNA_mPFC2_funcspace_thr0.95_UR, long_BNA_mPFC2_funcspace_thr0.95_R, long_BNA_mPFC2_funcspace_thr0.95_UR)



```


## Model 

Univariate activation ~ delay and congruency 
```{r, fig.height=5,fig.width=6}

### omnibus 
model<-lmer(uni_act ~ delay*condition + (1+CB_order|subj), data=mPFC_data, control = lmerControl(optimizer ="Nelder_Mead")) 

## check assumptions 
hist(residuals(model))
plot(model)
data2<-subset(mPFC_data, !is.na(uni_act)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$condition * data2$delay) ## heteroskedastic

# stats 
anova(model)
r.squaredGLMM(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")

```

# Hippocampi

## Create dataset for stats comparisons

R/UR trialwise univariate, only for detailed trials (used for hippocampi)
```{r}

# short and long delay 
delays<-c("short", "long")

# R= congruent, UR= incongruent 
conds<-c("R", "UR")

# ant and post masks 
masks<-c("R_ant_hippo_seg_funcspace_thr0.2", "R_post_hippo_seg_funcspace_thr0.2")

#subjects in CB1 counterbalancing condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")

for (delay in delays){
  for (cond in conds){
    for (mask in masks){
       data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/extracted_betas_trialwise/",cond,"_act_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
       colnames(data)<- c("subj", "trial", "mask", "uni_act")
       # add conditions 
       data$delay<-rep(delay, (nrow(data)))
       data$condition<-rep(cond, (nrow(data)))
       data$CB_order<-rep(2, nrow(data))
       # name participants consistently across sessions 
       for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
       # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        }
      }
       name<-paste(delay,mask,cond, sep="_")
       assign(name,data) #saves the mean and std under the current masks name
    }
  }
}

# create datasets 
hippo_right_ant_data<-rbind(short_R_ant_hippo_seg_funcspace_thr0.2_R,short_R_ant_hippo_seg_funcspace_thr0.2_UR,long_R_ant_hippo_seg_funcspace_thr0.2_R,long_R_ant_hippo_seg_funcspace_thr0.2_UR)

hippo_right_post_data<-rbind(short_R_post_hippo_seg_funcspace_thr0.2_R,short_R_post_hippo_seg_funcspace_thr0.2_UR,long_R_post_hippo_seg_funcspace_thr0.2_R,long_R_post_hippo_seg_funcspace_thr0.2_UR)


```

## Anterior Hippocampus 

### Models 
```{r, fig.height=5,fig.width=6}

#so this model has a random intercept for each subject. decided not to go with trials nested within subject because didnt add anything to the model when tested on mPFC model comparisons 

### omnibus 
model<-lmer(uni_act ~ delay*condition + (1+CB_order|subj), data=hippo_right_ant_data, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

## check assumptions 
hist(residuals(model))
plot(model)
data2<-subset(hippo_right_ant_data, !is.na(uni_act)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$condition * data2$delay) 
leveneTest(residuals(model) ~ data2$condition) 
leveneTest(residuals(model) ~ data2$delay) 

# stats 
anova(model)
r.squaredGLMM(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")

```


## Posterior Hippocampus
```{r, fig.height=5,fig.width=6}

### omnibus 
model<-lmer(uni_act ~ delay*condition + (1+CB_order|subj), data=hippo_right_post_data, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

## check model assumptions 
hist(residuals(model))
plot(model)
data2<-subset(hippo_right_post_data, !is.na(uni_act)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$condition * data2$delay)
leveneTest(residuals(model) ~ data2$condition)
leveneTest(residuals(model) ~ data2$delay)

# stats 
anova(model)
r.squaredGLMM(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")

```



