---
title: "Supplemental Method 1: Proportion of ‘Don’t Know’ versus Incorrect responses. "
output: html_notebook
---

Sam Audrain August 2022
V 2.0
 
# Packages
```{r}
library(ggplot2)
library(Rmisc)
```

# Read in and subset the data
```{r}

###### CHANGE PATH FOR YOUR DATA #######
data<-read.csv("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/SCP_behavioural_data.csv")
data$CB_order<-as.factor(data$CB_order)

# subset the data
data_fine<-subset(data, granularity == "fine")
data_coarse<-subset(data, granularity == "coarse")

```


# Supplementary Figure 1

## Context memory
### Don't know (responded "don't know" to context question)
```{r, fig.height=4.5,fig.width=4.5}

# summarize for plot 
stats<-summarySEwithin(data=data_coarse, measurevar = "DK_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
# add SE and condition information 
stats$upper_se<-stats$DK_perc + stats$se
stats$lower_se<-stats$DK_perc - stats$se
stats$forgot<-rep("DK_perc", length(stats$DK_perc))
colnames(stats)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")

# plot 
ggplot(stats, aes(x=delay, y=forgot_perc, fill=congruency)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  geom_point(data=data_coarse, position=position_jitterdodge(jitter.width=0.5, dodge.width = 0.8), pch=1, aes(delay, DK_perc, group=congruency), show.legend = F, size = 2)+
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank(), axis.text=element_text(size=18), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom") +
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("congruent","incongruent"))+ 
  labs(x= "", y="% forgotten (of total trials)", fill="") +
  ggtitle(" ")

```

### Incorrect (chose incorrect context)
```{r, fig.height=4.5,fig.width=4.5}

# summarize for plot 
stats2<-summarySEwithin(data=data_coarse, measurevar = "incorrect_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
# add SE and condition information 
stats2$upper_se<-stats2$incorrect_perc + stats2$se
stats2$lower_se<-stats2$incorrect_perc - stats2$se
stats2$forgot<-rep("incorrect_perc", length(stats2$incorrect_perc))
colnames(stats2)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")

# plot 
ggplot(stats2, aes(x=delay, y=forgot_perc, fill=congruency)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  geom_point(data=data_coarse, position=position_jitterdodge(jitter.width=0.5, dodge.width = 0.8), pch=1, aes(delay, incorrect_perc, group=congruency), show.legend = F, size = 2)+
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank(), axis.text=element_text(size=18), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("congruent","incongruent"))+ ## manuscript 
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  labs(x= "", y="% forgotten (of total trials)", fill="") +
  ggtitle(" ")

```

## Scene memory 
### Don't know (answered context question correct, answered "don't know" to scene question)
```{r, fig.height=4.5,fig.width=4.5}

# summarize for plot 
stats<-summarySEwithin(data=data_fine, measurevar = "DK_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
# add SE and condition information 
stats$upper_se<-stats$DK_perc + stats$se
stats$lower_se<-stats$DK_perc - stats$se
stats$forgot<-rep("DK_perc", length(stats$DK_perc))
colnames(stats)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")

# plot 
ggplot(stats, aes(x=delay, y=forgot_perc, fill=congruency)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  geom_point(data=data_fine, position=position_jitterdodge(jitter.width=0.5, dodge.width = 0.8), pch=1, aes(delay, DK_perc, group=congruency), show.legend = F, size = 2)+
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank(), axis.text=element_text(size=18), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("congruent","incongruent"))+ ## manuscript 
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  labs(x= "", y="% forgotten (of total trials)", fill="") +
  ggtitle(" ")

```

### Incorrect (answered context question correct, chose the incorrect scene)
```{r, fig.height=4.5,fig.width=4.5}

# summarize for plot 
stats2<-summarySEwithin(data=data_fine, measurevar = "incorrect_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
# add SE and condition information 
stats2$upper_se<-stats2$incorrect_perc + stats2$se
stats2$lower_se<-stats2$incorrect_perc - stats2$se
stats2$forgot<-rep("incorrect_perc", length(stats2$incorrect_perc))
colnames(stats2)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")

# plot 
ggplot(stats2, aes(x=delay, y=forgot_perc, fill=congruency)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  geom_point(data=data_fine, position=position_jitterdodge(jitter.width=0.5, dodge.width = 0.8), pch=1, aes(delay, incorrect_perc, group=congruency), show.legend = F, size = 2)+
 theme(axis.title = element_text(size=20), axis.ticks.x=element_blank(), axis.text=element_text(size=18), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("congruent","incongruent"))+ ## manuscript 
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  labs(x= "", y="% forgotten (of total trials)", fill="") +
  ggtitle(" ")


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

