---
title: "Supplementary Method 11: Pattern similarity broken down by scene category."
output: html_notebook
---
 
Sam Audrain August 2022
V 2.0 


# Packages
```{r}

library(lme4)
library(ggplot2)
library(emmeans)
library(psych)
library(Rmisc)
library(ggtext)

```


# mPFC

## Create dataset for stats comparisons 
- Correlations are fisher transformed into normal distributions for statistical comparison here 
- organizes within context and across context correlations (for mPFC)

```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("BNA_mPFC2")

# within context vs across context correlations 
grans<-c("wincon", "xcon")

#subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for (mask in masks){
        ###### CHANGE PATH FOR YOUR DATA ####### 
        data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_V8_cat/",cond,"_corrs_",gran,"_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
        colnames(data)<- c("subj", "trial", "mask", "R", "cat")
        data$R_fish<-fisherz(data$R) # fisher transformation
        # add condition information 
        data$condition<-rep(gran, (nrow(data)))
        data$delay<-rep(delay, (nrow(data)))
        data$congruency<-rep(cond, (nrow(data)))
        # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below. 
        data$CB_order<-rep(2, nrow(data))
        # make naming convention the same across delays for counterbalanced subjects 
        for (r in 1:nrow(data)){
          if (data[r,"subj"] == "P201_20181101"){
            data[r,"subj"]<-"P101_20181029"
          } else if (data[r,"subj"] == "S205_20181116"){
            data[r,"subj"]<-"S105_20181113"
          } else if (data[r,"subj"] == "S206_20181122"){
            data[r,"subj"]<-"S106_20181119"
          } else if (data[r,"subj"] == "S207_20181129"){
            data[r,"subj"]<-"S107_20181126"
          } else if (data[r,"subj"] == "S209_20190117"){
            data[r,"subj"]<-"S109_20190114"
          } else if (data[r,"subj"] == "S210_20190123"){
            data[r,"subj"]<-"S110_20190120"
          }
        }
        # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          } 
        }
        name<-paste(delay,mask,cond,gran,sep="_")
        assign(name,data) #saves the mean and std under the current masks name
      }
    }
  }
}


# create dataset 
mPFC_data<-rbind(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_R_xcon,short_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_UR_xcon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_UR_xcon)

# cleanup enviro 
rm(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_R_xcon,short_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_UR_xcon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_UR_xcon)


```

## Plot Beaches

```{r, fig.height=4,fig.width=4}

# subset the data 
mPFC_data_beach<-subset(mPFC_data, cat != "KK")

# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=mPFC_data_beach, na.action=na.omit) 

# summarize data 
table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay), adjust = "none"))
colnames(table)<-c("condition", "congruency", "delay", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
table<-subset(table, contrast == ".")

stats<-summarySEwithin(data=mPFC_data_beach, measurevar = "R_fish", withinvars = c("delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset, and correct se 
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

# plot 
ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#2C3E50","#5D6D7E","#85929E","#D5D8DC"), labels = c("congruent within", "congruent across", "incongruent within","incongruent across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.08,0.01),expand = c(0, 0), limits = c(0,0.08))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("mPFC beaches")


```


## Plot Kitchens

```{r, fig.height=4,fig.width=4}

# subset the data 
mPFC_data_kitchen<-subset(mPFC_data, cat != "BB")

# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=mPFC_data_kitchen, na.action=na.omit) 

# summarize data 
table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay), adjust = "none"))
colnames(table)<-c("condition", "congruency", "delay", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
table<-subset(table, contrast == ".")

stats<-summarySEwithin(data=mPFC_data_kitchen, measurevar = "R_fish", withinvars = c("delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset, and correct se 
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

# plot 
ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#2C3E50","#5D6D7E","#85929E","#D5D8DC"), labels = c("congruent within kitch.", "congruent across", "incongruent within kitch.","incongruent across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.08,0.01),expand = c(0, 0), limits = c(0,0.08))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("mPFC kitchens")

```

# Hippocampi 

## Create datasets for stats comparisons, on detailed mems 
```{r}


# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("right_hippo_ant", "right_hippo_post")

# condition: same scene, similar scene, and cross context correlations
grans<-c("simscene", "samescene", "xcon")

# for memories remembered with fine granularity/detail only
grans2<-c("fine")

# subjects in CB1 counterbalancing condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for(gran2 in grans2){
        for (mask in masks){
          ###### CHANGE PATH FOR YOUR DATA #######
          data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_V8_cat/",cond,"_corrs_",gran,"_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
          colnames(data)<- c("subj", "trial", "mask", "R", "cat")
          data$R_fish<-fisherz(data$R) # fisher transformation
          # add conditions 
          data$condition<-rep(gran, (nrow(data)))
          data$delay<-rep(delay, (nrow(data)))
          data$congruency<-rep(cond, (nrow(data)))
          # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
        data$CB_order<-rep(2, nrow(data))
          # ensure consistent naming of counterbalanced subjects
          for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
         # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          }
        }
          name<-paste(delay,mask,cond,gran,gran2,sep="_")
          assign(name,data) #saves the mean and std under the current masks name
        }
      }
    }
  }
}


#create right ant hippo dataset
hippo_right_ant_data_fine<-rbind(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

#create right post hippo dataset
hippo_right_post_data_fine<-rbind(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

# clean up enviro
rm(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

rm(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)


```

## Right anterior hippocampus

### Plot Beaches

```{r, fig.height=4,fig.width=4}

# subset the data 
hippo_right_ant_data_fine_beaches<-subset(hippo_right_ant_data_fine, cat != "K1K2" & cat != "K2K1" & cat != "K1K1" & cat != "K2K2")

# model to plot 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_ant_data_fine_beaches, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

# summarize the data 
eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay), adjust = "none"))
colnames(eff_interaction)<-c("condition", "delay", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
eff_interaction<-subset(eff_interaction, contrast == ".")
#grab within-subject error bars 
stats<-summarySEwithin(data=hippo_right_ant_data_fine_beaches, measurevar = "R_fish", withinvars = c("delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset, and correct se 
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

#plot 
ggplot(stats, aes(x=delay, y=emmean, fill=condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#5D6D7E","#85929E","#D5D8DC"), labels = c("same scene", "similar scene", "other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.06,0.01), expand = c(0, 0), limits = c(0,0.06))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("AH beaches
          ")

```


### Plots Kitchens

```{r, fig.height=4,fig.width=4}

# subset the data 
hippo_right_ant_data_fine_kitchens<-subset(hippo_right_ant_data_fine, cat != "B1B2" & cat != "B2B1" & cat != "B1B1" & cat != "B2B2")

# model
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_ant_data_fine_kitchens, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

# summarize the data 
eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay), adjust = "none"))
colnames(eff_interaction)<-c("condition", "delay", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
eff_interaction<-subset(eff_interaction, contrast == ".")
#grab within-subject error bars 
stats<-summarySEwithin(data=hippo_right_ant_data_fine_kitchens, measurevar = "R_fish", withinvars = c("delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

#plot 
ggplot(stats, aes(x=delay, y=emmean, fill=condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#5D6D7E","#85929E","#D5D8DC"), labels = c("same scene", "similar scene", "other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.06,0.01), expand = c(0, 0), limits = c(0,0.06))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("AH kitchens
          ")

```

## Right posterior hippocampus

### Plot Beaches

```{r, fig.height=4,fig.width=4}

# subset the data 
hippo_right_post_data_fine_beaches<-subset(hippo_right_post_data_fine, cat != "K1K2" & cat != "K2K1" & cat != "K1K1" & cat != "K2K2")

# model to plot 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_post_data_fine_beaches, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

# summarize the data 
eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay), adjust = "none"))
colnames(eff_interaction)<-c("condition", "delay", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
eff_interaction<-subset(eff_interaction, contrast == ".")
#grab within-subject error bars 
stats<-summarySEwithin(data=hippo_right_post_data_fine_beaches, measurevar = "R_fish", withinvars = c("delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset, and correct se 
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

#plot 
ggplot(stats, aes(x=delay, y=emmean, fill=condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#5D6D7E","#85929E","#D5D8DC"), labels = c("same scene", "similar scene", "other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.06,0.01), expand = c(0, 0), limits = c(0,0.06))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("PH beaches
          ")

```


### Plots Kitchens

```{r, fig.height=4,fig.width=4}

# subset the data 
hippo_right_post_data_fine_kitchens<-subset(hippo_right_post_data_fine, cat != "B1B2" & cat != "B2B1" & cat != "B1B1" & cat != "B2B2")

# model
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_post_data_fine_kitchens, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

# summarize the data 
eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay), adjust = "none"))
colnames(eff_interaction)<-c("condition", "delay", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
eff_interaction<-subset(eff_interaction, contrast == ".")
#grab within-subject error bars 
stats<-summarySEwithin(data=hippo_right_post_data_fine_kitchens, measurevar = "R_fish", withinvars = c("delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

#plot 
ggplot(stats, aes(x=delay, y=emmean, fill=condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#5D6D7E","#85929E","#D5D8DC"), labels = c("same scene", "similar scene", "other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.06,0.01), expand = c(0, 0), limits = c(0,0.06))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("PH kitchens
          ")

```