---
title: "SCP Univariate Control Analysis"
output: html_notebook
---

Trialwise univariate activation was extracted from the mPFC (for trials where got context correct) and hippocampi (for trials where got context and scene correct). Here, we test for effects of congruency and delay on univariate activation.

# Load packages 
```{r}

library(psych)
library(lme4)
library(nlme)
library(ggplot2)
library(effects)
library(emmeans)
library(Rmisc)

```

# Create dataset for stats comparisons, R/UR trialwise univariate, regardless of detail (used for mPFC)

```{r}


delays<-c("short", "long")

conds<-c("R", "UR")

masks<-c("BNA_mPFC2_funcspace_thr0.95")

#subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")

for (delay in delays){
  for (cond in conds){
    for (mask in masks){
       data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/extracted_betas_trialwise/",cond,"_act_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
       colnames(data)<- c("subj", "trial", "mask", "uni_act")
       data$delay<-rep(delay, (nrow(data)))
       data$condition<-rep(cond, (nrow(data)))
       data$CB_order<-rep(2, nrow(data))
       for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
       # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        }
      }
       name<-paste(delay,mask,cond, sep="_")
       assign(name,data) #saves the mean and std under the current masks name
    }
  }
}

mPFC_data<-rbind(short_BNA_mPFC2_funcspace_thr0.95_R, short_BNA_mPFC2_funcspace_thr0.95_UR, long_BNA_mPFC2_funcspace_thr0.95_R, long_BNA_mPFC2_funcspace_thr0.95_UR)



```


## mPFC 

Univariate activation ~ delay and congruency 
```{r, fig.height=5,fig.width=6}

### omnibus 
model<-lmer(uni_act ~ delay*condition + (1+CB_order|subj), data=mPFC_data, control = lmerControl(optimizer ="Nelder_Mead")) 

## check assumptions 
hist(residuals(model))
plot(model)
data2<-subset(mPFC_data, !is.na(uni_act)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$condition * data2$delay) ## heteroskedastic

anova(model)
```


# Create dataset for stats comparisons, R/UR trialwise univariate, only for detailed trials (used for hippocampi)

```{r}

delays<-c("short", "long")

conds<-c("R", "UR")

masks<-c("R_ant_hippo_seg_funcspace_thr0.2", "R_post_hippo_seg_funcspace_thr0.2")

#subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")

for (delay in delays){
  for (cond in conds){
    for (mask in masks){
       data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/extracted_betas_trialwise/",cond,"_act_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
       colnames(data)<- c("subj", "trial", "mask", "uni_act")
       data$delay<-rep(delay, (nrow(data)))
       data$condition<-rep(cond, (nrow(data)))
       data$CB_order<-rep(2, nrow(data))
       for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
       # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        }
      }
       name<-paste(delay,mask,cond, sep="_")
       assign(name,data) #saves the mean and std under the current masks name
    }
  }
}

hippo_right_ant_data<-rbind(short_R_ant_hippo_seg_funcspace_thr0.2_R,short_R_ant_hippo_seg_funcspace_thr0.2_UR,long_R_ant_hippo_seg_funcspace_thr0.2_R,long_R_ant_hippo_seg_funcspace_thr0.2_UR)

hippo_right_post_data<-rbind(short_R_post_hippo_seg_funcspace_thr0.2_R,short_R_post_hippo_seg_funcspace_thr0.2_UR,long_R_post_hippo_seg_funcspace_thr0.2_R,long_R_post_hippo_seg_funcspace_thr0.2_UR)


```

## Anterior Hippocampus 
```{r, fig.height=5,fig.width=6}

#so this model has a random intercept for each subject. decided not to go with trials nested within subject because didnt add anything to the model when tested on mPFC model comparisons 

### omnibus 
model<-lmer(uni_act ~ delay*condition + (1+CB_order|subj), data=hippo_right_ant_data, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

## check assumptions 
hist(residuals(model))
plot(model)
data2<-subset(hippo_right_ant_data, !is.na(uni_act)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$condition * data2$delay) 
leveneTest(residuals(model) ~ data2$condition) 
leveneTest(residuals(model) ~ data2$delay) 

anova(model)

```


## Posterior Hippocampus
```{r, fig.height=5,fig.width=6}

### omnibus 
model<-lmer(uni_act ~ delay*condition + (1+CB_order|subj), data=hippo_right_post_data, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

## check model assumptions 
hist(residuals(model))
plot(model)
data2<-subset(hippo_right_post_data, !is.na(uni_act)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$condition * data2$delay)
leveneTest(residuals(model) ~ data2$condition)
leveneTest(residuals(model) ~ data2$delay)

anova(model)

```



