---
title: "Supplementary Method 7: Integration of arbitrary objects only"
output: html_notebook
---

Sam Audrain August 2022
V 2.0


This script computes statistical comparisons between patterns for correctly retrieved incongruent trials in mPFC where the objects were arbitrary (i.e. there were no kitchen or beach objects). This is a Supplementary Analysis to control for relatedness between objects and opposing contexts with which they were correlated in the Object Similarity analysis. 

In all cases, objects are incongruent with the background, and with each other. There is no semantic similarity between objects. 

# Read in required packages
```{r}
library(nlme)
library(lme4)
library(ggplot2)
library(emmeans)
library(Rmisc)
library(psych)
library(car)
library(lmerTest)
library(ggtext)
library(MuMIn)

```

# Create dataset for stats comparisons 
- Correlations are fisher transformed into normal distributions for statistical comparison here 

```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# within = within context correlations, across = across context correlations 
conds<-c("within", "across")

# ROIs
masks<-c("BNA_mPFC2")

#subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")

for (delay in delays){
  for (cond in conds){
    for (mask in masks){
      ###### CHANGE PATH FOR YOUR DATA ####### 
      data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/arbO_",cond,"_corrs_zscored_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
      colnames(data)<- c("subj", "trial", "mask", "R")
      data$R_fish<-fisherz(data$R) # fisher transform 
      # add condition information 
      data$delay<-rep(delay, (nrow(data)))
      data$cond<-rep(cond, (nrow(data)))
      # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below. 
      data$CB_order<-rep(2, nrow(data))
      # make naming convention the same across delays for counterbalanced subjects 
      for (r in 1:nrow(data)){
        if (data[r,"subj"] == "P201_20181101"){
          data[r,"subj"]<-"P101_20181029"
        } else if (data[r,"subj"] == "S205_20181116"){
          data[r,"subj"]<-"S105_20181113"
        } else if (data[r,"subj"] == "S206_20181122"){
          data[r,"subj"]<-"S106_20181119"
        } else if (data[r,"subj"] == "S207_20181129"){
          data[r,"subj"]<-"S107_20181126"
        } else if (data[r,"subj"] == "S209_20190117"){
          data[r,"subj"]<-"S109_20190114"
        } else if (data[r,"subj"] == "S210_20190123"){
          data[r,"subj"]<-"S110_20190120"
        }
      }
      # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        } 
      }
      name<-paste(delay,mask,cond,sep="_")
      assign(name,data) #saves the mean and std under the current masks name
    }
  }
}


# create dataset 
mPFC_data<-rbind(short_BNA_mPFC2_across, long_BNA_mPFC2_across, short_BNA_mPFC2_within, long_BNA_mPFC2_within)

# cleanup enviro
rm(short_BNA_mPFC2_within, short_BNA_mPFC2_across, long_BNA_mPFC2_within, long_BNA_mPFC2_across)




```

# Model 
```{r, fig.height=5,fig.width=4.5}

######### initital model fits #########
# model 
# model<-lmer(R_fish ~ cond*delay + (1+CB_order|subj), data=mPFC_data, na.action=na.omit) 
# 
# hist(residuals(model))
# #check for homogeneity of variance
# plot(model)#should look fairly uniform and random. Possible heteroskedasticity? 
# data2<-subset(mPFC_data, !is.na(R_fish)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
# leveneTest(residuals(model) ~ data2$cond * data2$delay) ## heteroskedastic

######## final model fit #############
# adding weights to allow variance to vary across condiiton and delay 
model<-lme(R_fish ~ cond * delay, random = ~1+CB_order|subj, data=mPFC_data, na.action=na.omit, weights=varIdent(form=~1|cond*delay))
hist(residuals(model)) #check residuals

# model stats 
anova(model)
intervals(model, level=0.95, which="fixed")
r.squaredGLMM(model)

# post hoc
pairwise<-emmeans(model,list(pairwise ~ delay), adjust = "none", lmer.df = "satterthwaite") 
pairwise
confint(pairwise, level=0.95, oldNames=FALSE, method="boot")

```
# Plot 

Supplementary Fig. 7
```{r, fig.height=5,fig.width=4.5}

# summarize the data 
## use estimated marginal means 
eff_interaction <-emmeans(model, specs = c("delay","cond")) #se is not for within subject data here
eff_interaction_df <- as.data.frame(eff_interaction)
## use within subject se 
stats<-summarySEwithin(data=mPFC_data, measurevar = "R_fish", withinvars = c("cond","delay"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset, with correct se 
stats$emmean<-eff_interaction_df$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

# get conditions in proper order 
stats$cond = factor(stats$cond, levels=c("within","across"))

# plot 
ggplot(stats, aes(x=delay, y=emmean, fill=cond)) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color="black") + 
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom",axis.title.y = ggtext::element_markdown()) + 
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels = c("within", "across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.08,0.01), expand = c(0, 0), limits = c(0,0.08))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("mPFC")


```
