---
title: "Supplementary Method 10: Pattern similarity of forgotten trials"
output: html_notebook
---

This script runs the main analyses in the manuscript for mPFC and hippocampal ROIs, but on forgotten trials rather than remembered trials. 

Sam Audrain August 2022
V 2.0

# Load Packages
```{r}

library(psych)
library(lme4)
library(nlme)
library(ggplot2)
library(emmeans)
library(Rmisc)
library(car)
library(lmerTest)
library(ggtext)
library(MuMIn)


```

# mPFC 
For the mPFC we use Within vs Across Context Correlations (not broken down by same/sim/other, as in the main manuscript)

## Create datasets

Forgotten and remembered trials for within vs across context correlations 

Also fisher transforming the correlations into normal distributions so can statistically compare 

```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("BNA_mPFC2")

# condition: wincon = within context and xcon = across context correlations 
grans<-c("wincon", "xcon")

# subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")

########## forgotten trials ###############
for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for (mask in masks){
        ###### CHANGE PATH FOR YOUR DATA #######
        data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/forgot_",cond,"_corrs_",gran,"_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
        colnames(data)<- c("subj", "trial", "mask", "R")
        data$R_fish<-fisherz(data$R) # fisher z score 
        # add conditions 
        data$condition<-rep(gran, (nrow(data)))
        data$delay<-rep(delay, (nrow(data)))
        data$congruency<-rep(cond, (nrow(data)))
        # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
      data$CB_order<-rep(2, nrow(data))
        # ensure consistent naming of counterbalanced subjects
        for (r in 1:nrow(data)){
          if (data[r,"subj"] == "P201_20181101"){
            data[r,"subj"]<-"P101_20181029"
          } else if (data[r,"subj"] == "S205_20181116"){
            data[r,"subj"]<-"S105_20181113"
          } else if (data[r,"subj"] == "S206_20181122"){
            data[r,"subj"]<-"S106_20181119"
          } else if (data[r,"subj"] == "S207_20181129"){
            data[r,"subj"]<-"S107_20181126"
          } else if (data[r,"subj"] == "S209_20190117"){
            data[r,"subj"]<-"S109_20190114"
          } else if (data[r,"subj"] == "S210_20190123"){
            data[r,"subj"]<-"S110_20190120"
          }
        }
       # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        }
      }
        name<-paste(delay,mask,cond,gran,sep="_")
        assign(name,data) #saves the mean and std under the current masks name
      }
    }
  }
}

# create datasets 
# within context correlation datasets
mPFC_data_wincon_forgot<-rbind(short_BNA_mPFC2_R_wincon, short_BNA_mPFC2_UR_wincon, long_BNA_mPFC2_R_wincon, long_BNA_mPFC2_UR_wincon)

# within and across context correlation datasets 
mPFC_data_forgot<-rbind(short_BNA_mPFC2_R_wincon, short_BNA_mPFC2_UR_wincon, long_BNA_mPFC2_R_wincon, long_BNA_mPFC2_UR_wincon, short_BNA_mPFC2_R_xcon, short_BNA_mPFC2_UR_xcon, long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_xcon)



########## remembered trials ###############
for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for (mask in masks){
        ###### CHANGE PATH FOR YOUR DATA ####### 
        data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/",cond,"_corrs_",gran,"_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
        colnames(data)<- c("subj", "trial", "mask", "R")
        data$R_fish<-fisherz(data$R)
        data$condition<-rep(gran, (nrow(data)))
        data$delay<-rep(delay, (nrow(data)))
        data$congruency<-rep(cond, (nrow(data)))
        data$mem<-rep("remem", (nrow(data)))
        # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below. 
        data$CB_order<-rep(2, nrow(data))
        # make naming convention the same across delays for counterbalanced subjects 
        for (r in 1:nrow(data)){
          if (data[r,"subj"] == "P201_20181101"){
            data[r,"subj"]<-"P101_20181029"
          } else if (data[r,"subj"] == "S205_20181116"){
            data[r,"subj"]<-"S105_20181113"
          } else if (data[r,"subj"] == "S206_20181122"){
            data[r,"subj"]<-"S106_20181119"
          } else if (data[r,"subj"] == "S207_20181129"){
            data[r,"subj"]<-"S107_20181126"
          } else if (data[r,"subj"] == "S209_20190117"){
            data[r,"subj"]<-"S109_20190114"
          } else if (data[r,"subj"] == "S210_20190123"){
            data[r,"subj"]<-"S110_20190120"
          }
        }
        # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          } 
        }
        name<-paste(delay,mask,cond,gran,sep="_")
        assign(name,data) #saves the mean and std under the current masks name
      }
    }
  }
}


# create datasets 
# within context correlation datasets
mPFC_data_wincon<-rbind(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_UR_wincon)

# within and across context correlation datasets 
mPFC_data<-rbind(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_R_xcon,short_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_UR_xcon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_UR_xcon)

# clean up environment 
rm(short_BNA_mPFC2_R_wincon, short_BNA_mPFC2_UR_wincon, long_BNA_mPFC2_R_wincon, long_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_R_xcon, short_BNA_mPFC2_UR_xcon, long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_xcon)


```


### Combine remembered and forgotten datasets 
```{r}
# add a memory condition column to forgotten datasets 
mPFC_data_forgot$mem<-rep("forgot", (nrow(mPFC_data_forgot)))
mPFC_data_wincon_forgot$mem<-rep("forgot", (nrow(mPFC_data_wincon_forgot)))

# combine them 
mPFC_data2<-rbind(mPFC_data, mPFC_data_forgot)
mPFC_data_wincon2<-rbind(mPFC_data_wincon, mPFC_data_wincon_forgot)

#rm(mPFC_data, mPFC_data_forgot, mPFC_data_wincon, mPFC_data_wincon_forgot)

```


## Models

Re-running same models in the mPFC as on remembered trials in main manuscript, but on forgotten trials. 

### Within-context model 
```{r, fig.height=5,fig.width=4.5}

# model 
model<-lmer(R_fish ~ congruency*delay + (1+CB_order|subj), data=mPFC_data_wincon_forgot, na.action=na.omit,control = lmerControl(optimizer ="Nelder_Mead"))

# check model assumptions
hist(residuals(model))
plot(model)

# model stats 
anova(model)
r.squaredGLMM(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)


```

### Within vs across context models for each congruency 

#### Congruent 
```{r}
# subset the data 
mPFC_data_forgot_R<-subset(mPFC_data_forgot, congruency=="R")

# model 
model<-lmer(R_fish ~ condition*delay + (1+CB_order|subj), data=mPFC_data_forgot_R, na.action=na.omit)

# check model assumptions
hist(residuals(model))
plot(model)

# stats 
anova(model)
r.squaredGLMM(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)

# post hocs 
pairwise<-emmeans(model, list(pairwise ~ condition:delay), adjust = "none", lmer.df = "satterthwaite")
pairwise
confint(pairwise, level=0.95, oldNames=FALSE, method="boot")

```

#### Incongruent 
```{r}
# subset the data 
mPFC_data_forgot_UR<-subset(mPFC_data_forgot, congruency=="UR")

# model 
model<-lmer(R_fish ~ condition*delay + (1+CB_order|subj), data=mPFC_data_forgot_UR, na.action=na.omit)

# check model assumptions
hist(residuals(model))
plot(model)

# stats 
anova(model)
r.squaredGLMM(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)

```

### Running remem vs forgotten at long delay 

```{r}
# subset the data 
mPFC_data2_long<-subset(mPFC_data2, delay=="long")

# model 
model<-lmer(R_fish ~ mem*congruency*condition + (1+CB_order|subj), data=mPFC_data2_long, na.action=na.omit,control = lmerControl(optimizer ="Nelder_Mead"))

# check model assumptions
hist(residuals(model))
plot(model)

# stats 
anova(model)
r.squaredGLMM(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)

```


## Plots

Supplementary Fig.9 mPFC
```{r, fig.height=5.5,fig.width=7}

# model to plot 
model<-lmer(R_fish ~ condition*congruency*delay*mem + (1|subj), data=mPFC_data2, na.action=na.omit) 

# prepare for plotting 
table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay:mem), adjust = "none"))
colnames(table)<-c("condition","congruency", "delay", "mem", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
table<-subset(table, contrast == ".")

# summarize the data 
stats<-summarySEwithin(data=mPFC_data2, measurevar = "R_fish", withinvars = c("mem","delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset, and proper se 
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

# plot 
ggplot(stats, aes(x=delay:mem, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#2C3E50","#5D6D7E","#85929E","#D5D8DC"), labels = c("congruent within", "congruent across", "incongruent within","incongruent across"))+
  scale_x_discrete(limits=c("short:remem", "short:forgot","long:remem","long:forgot"), labels=c("short remem", "short forgot", "long remem", "long forgot"))+
  scale_y_continuous(breaks = seq(-0.08,0.08,0.01),expand = c(0, 0), limits = c(-0.08,0.08))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("mPFC")


```



# Hippocampi 

## Create datasets 

Same/Sim/Other correlations (used for hippocampi)
```{r}
# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("right_hippo_ant", "right_hippo_post")

# condition: same scene, similar scene, and across context correlations
grans<-c("simscene", "samescene", "xcon")

# detailed trials 
gran2<-c("fine")

# subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")

########## forgotten trials ##############
for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for (mask in masks){
        ###### CHANGE PATH FOR YOUR DATA #######
        data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/forgot_",cond,"_corrs_",gran,"_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
        colnames(data)<- c("subj", "trial", "mask", "R")
        data$R_fish<-fisherz(data$R) # fisher transform
        # add conditions 
        data$condition<-rep(gran, (nrow(data)))
        data$delay<-rep(delay, (nrow(data)))
        data$congruency<-rep(cond, (nrow(data)))
        # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
      data$CB_order<-rep(2, nrow(data))
        # ensure consistent naming of counterbalanced subjects
        for (r in 1:nrow(data)){
          if (data[r,"subj"] == "P201_20181101"){
            data[r,"subj"]<-"P101_20181029"
          } else if (data[r,"subj"] == "S205_20181116"){
            data[r,"subj"]<-"S105_20181113"
          } else if (data[r,"subj"] == "S206_20181122"){
            data[r,"subj"]<-"S106_20181119"
          } else if (data[r,"subj"] == "S207_20181129"){
            data[r,"subj"]<-"S107_20181126"
          } else if (data[r,"subj"] == "S209_20190117"){
            data[r,"subj"]<-"S109_20190114"
          } else if (data[r,"subj"] == "S210_20190123"){
            data[r,"subj"]<-"S110_20190120"
          }
        }
       # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        }
      }
        name<-paste(delay,mask,cond,gran,gran2,sep="_")
        assign(name,data) #saves the mean and std under the current masks name
      }
    }
  }
}


#create ant hippo dataset
hippo_right_ant_data_fine_forgot<-rbind(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

#create post hippo dataset
hippo_right_post_data_fine_forgot<-rbind(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

# clean up enviro
rm(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine) 

rm(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

grans2<-c("fine")

########## remembered trials ##############
for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for(gran2 in grans2){
        for (mask in masks){
          ###### CHANGE PATH FOR YOUR DATA #######
          data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/",cond,"_corrs_",gran,"_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
          colnames(data)<- c("subj", "trial", "mask", "R")
          data$R_fish<-fisherz(data$R) # fisher transform the data
          # add condition info 
          data$condition<-rep(gran, (nrow(data)))
          data$delay<-rep(delay, (nrow(data)))
          data$congruency<-rep(cond, (nrow(data)))
          data$mem<-rep("remem", (nrow(data)))
          # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
        data$CB_order<-rep(2, nrow(data))
          # ensure consistent naming of counterbalanced subjects
          for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
         # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          }
        }
          name<-paste(delay,mask,cond,gran,gran2,sep="_")
          assign(name,data) #saves the mean and std under the current masks name
        }
      }
    }
  }
}


#create right ant hippo dataset
hippo_right_ant_data_fine<-rbind(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)


#create right post hippo dataset
hippo_right_post_data_fine<-rbind(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)


# clean up enviro
rm(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

rm(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

```


### Combine datasets 
```{r}

hippo_right_ant_data_fine_forgot$mem<-rep("forgot", (nrow(hippo_right_ant_data_fine_forgot)))
hippo_right_post_data_fine_forgot$mem<-rep("forgot", (nrow(hippo_right_post_data_fine_forgot)))


hippo_right_ant_data_fine2<-rbind(hippo_right_ant_data_fine, hippo_right_ant_data_fine_forgot)
hippo_right_post_data_fine2<-rbind(hippo_right_post_data_fine, hippo_right_post_data_fine_forgot)


#rm(hippo_right_ant_data_fine, hippo_right_ant_data_forgot, hippo_right_post_data_fine, hippo_right_post_data_forgot)

```

## Anterior hippocampus 

### Models

#### Pattern similarity of forgotten trials over time 
```{r, fig.height=5,fig.width=4.5}
### omnibus model 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_ant_data_fine_forgot, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

# check model assumptions 
hist(residuals(model)) #should be normal, looks good 
plot(model)#should look fairly uniform and random, looks good 

# stats 
anova(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)
r.squaredGLMM(model)

```

#### Pattern similarity of remem vs forgotten at long delay 
```{r}
# subset the data 
hippo_right_ant_data_fine_long<-subset(hippo_right_ant_data_fine2, delay=="long")

# model 
model<-lmer(R_fish ~ mem*congruency*condition + (1+CB_order|subj), data=hippo_right_ant_data_fine_long, na.action=na.omit,control = lmerControl(optimizer ="Nelder_Mead"))

# check model assumptions
hist(residuals(model))
plot(model)
# # test heteroskedasticity with levene's test
data2<-subset(hippo_right_ant_data_fine_long, !is.na(R_fish)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$congruency * data2$condition *data2$mem) 
leveneTest(residuals(model) ~ data2$congruency * data2$condition) 
leveneTest(residuals(model) ~ data2$congruency * data2$mem) 
leveneTest(residuals(model) ~ data2$mem * data2$condition) 

# stats 
anova(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)
r.squaredGLMM(model)

```

### Plot 

Supplementary Fig.9 
```{r, fig.height=5.5,fig.width=7}

# model to plot 
model<-lmer(R_fish ~ condition*congruency*delay*mem + (1|subj), data=hippo_right_ant_data_fine2, na.action=na.omit) 

# prepare for plotting
table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay:mem), adjust = "none"))
colnames(table)<-c("condition","congruency", "delay", "mem", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
table<-subset(table, contrast == ".")

# summarize data 
stats<-summarySEwithin(data=hippo_right_ant_data_fine2, measurevar = "R_fish", withinvars = c("mem","delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

# plot 
ggplot(stats, aes(x=delay:mem, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("C same scene", "C similar scene", "C other context", "IC same scene", "IC similar scene", "IC other context"))+
  scale_x_discrete(limits=c("short:remem", "short:forgot","long:remem","long:forgot"), labels=c("short remem", "short forgot", "long remem", "long forgot"))+
  scale_y_continuous(breaks = seq(-0.08,0.08,0.01),expand = c(0, 0), limits = c(-0.08,0.08))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("anterior hippocampus")

```


## Posterior hippocampus 

### Models

#### Pattern similarity of forgotten trials over time 
```{r, fig.height=5,fig.width=4.5}
### omnibus 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_post_data_fine_forgot, na.action=na.omit)

## check assumptions 
hist(residuals(model)) #should be normal, looks good 
plot(model)#should look fairly uniform and random, looks good 

# stats 
anova(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)
r.squaredGLMM(model)

```

#### Pattern similarity of remem vs forgotten at long delay 
```{r}
# subset the data 
hippo_right_post_data_fine_long<-subset(hippo_right_post_data_fine2, delay=="long")

# model 
model<-lmer(R_fish ~ mem*congruency*condition + (1+CB_order|subj), data=hippo_right_post_data_fine_long, na.action=na.omit,control = lmerControl(optimizer ="Nelder_Mead"))

# check model assumptions
hist(residuals(model))
plot(model)

# stats
anova(model)
confint(model, level=0.95, oldNames=FALSE, method="boot")
fixef(model)
r.squaredGLMM(model)

```

### Plot
Supplementary Fig.9 
```{r, fig.height=5.5,fig.width=7}

# model to plot
model<-lmer(R_fish ~ condition*congruency*delay*mem + (1|subj), data=hippo_right_post_data_fine2, na.action=na.omit) 

# prepare for plotting
table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay:mem), adjust = "none"))
colnames(table)<-c("condition","congruency", "delay", "mem", "contrast", "emmean", "SE", "df", "asymp.LCL", "asymp.UCL")
table<-subset(table, contrast == ".")

# summarize
stats<-summarySEwithin(data=hippo_right_post_data_fine2, measurevar = "R_fish", withinvars = c("mem","delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

# plot 
ggplot(stats, aes(x=delay:mem, y=emmean, fill=congruency:condition)) +
theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("C same scene", "C similar scene", "C other context", "IC same scene", "IC similar scene", "IC other context"))+
  scale_x_discrete(limits=c("short:remem", "short:forgot","long:remem","long:forgot"), labels=c("short remem", "short forgot", "long remem", "long forgot"))+
  scale_y_continuous(breaks = seq(-0.08,0.08,0.01),expand = c(0, 0), limits = c(-0.08,0.08))+
  geom_hline(yintercept=0)+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  ggtitle("posterior hippocampus")


```



