---
title: "SCP RSA Modelling Forgotten Trials"
output: html_notebook
---

# Load Packages
```{r}

library(psych)
library(lme4)
library(nlme)
library(ggplot2)
library(effects)
library(emmeans)
library(Rmisc)
library(car)
library(lmerTest)

```

# Within vs Across Context Correlations (not broken down by same/sim/other; used for mPFC)

## Load in data
Forgotten trials for within vs across context correlations 

Create dataset for stats comparisons, R/UR forgotten.
Also fisher transforming the correlations into normal distributions so can statistically compare 

```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("BNA_mPFC2")

# condition: same scene, similar scene, and cross context correlations
grans<-c("wincon", "xcon")

# for memories remembered with fine granularity/detail only
grans2<-c("fine")

# subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for(gran2 in grans2){
        for (mask in masks){
          ###### CHANGE PATH FOR YOUR DATA #######
          data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/forgot_",cond,"_corrs_",gran,"_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
          colnames(data)<- c("subj", "trial", "mask", "R")
          data$R_fish<-fisherz(data$R)
          data$condition<-rep(gran, (nrow(data)))
          data$delay<-rep(delay, (nrow(data)))
          data$congruency<-rep(cond, (nrow(data)))
          # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
        data$CB_order<-rep(2, nrow(data))
          # ensure consistent naming of counterbalanced subjects
          for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
         # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          }
        }
          name<-paste(delay,mask,cond,gran,sep="_")
          assign(name,data) #saves the mean and std under the current masks name
        }
      }
    }
  }
}



mPFC_data_forgot<-rbind(short_BNA_mPFC2_R_wincon, short_BNA_mPFC2_UR_wincon, long_BNA_mPFC2_R_wincon, long_BNA_mPFC2_UR_wincon, short_BNA_mPFC2_R_xcon, short_BNA_mPFC2_UR_xcon, long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_xcon)

mPFC_data_wincon_forgot<-rbind(short_BNA_mPFC2_R_wincon, short_BNA_mPFC2_UR_wincon, long_BNA_mPFC2_R_wincon, long_BNA_mPFC2_UR_wincon)


rm(short_BNA_mPFC2_R_wincon, short_BNA_mPFC2_UR_wincon, long_BNA_mPFC2_R_wincon, long_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_R_xcon, short_BNA_mPFC2_UR_xcon, long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_xcon)


```


## mPFC

### Models

Re-running same models as on remembered trials. 

Within-context model 
```{r, fig.height=5,fig.width=4.5}

model<-lmer(R_fish ~ congruency*delay + (1+CB_order|subj), data=mPFC_data_wincon_forgot, na.action=na.omit,control = lmerControl(optimizer ="Nelder_Mead"))

# check model assumptions
hist(residuals(model))
plot(model)

anova(model)
```

Congruent within vs across
```{r}
### congruent ###
mPFC_data_forgot_R<-subset(mPFC_data_forgot, congruency=="R")

# model 
model<-lmer(R_fish ~ condition*delay + (1+CB_order|subj), data=mPFC_data_forgot_R, na.action=na.omit)

# check model assumptions
hist(residuals(model))
plot(model)

anova(model)
emmeans(model, list(pairwise ~ condition:delay), adjust = "none", lmer.df = "satterthwaite")
```

Incongruent within vs across 
```{r}
### incongruent ###
mPFC_data_forgot_UR<-subset(mPFC_data_forgot, congruency=="UR")

# model 
model<-lmer(R_fish ~ condition*delay + (1+CB_order|subj), data=mPFC_data_forgot_UR, na.action=na.omit)

# check model assumptions
hist(residuals(model))
plot(model)

anova(model)

```

### Plots

Supplementary Fig.9 mPFC
```{r, fig.height=5,fig.width=4.5}

# prepare for plotting
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=mPFC_data_forgot, na.action=na.omit) 

table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay), adjust = "none"))
table<-subset(table, contrast == ".")

stats<-summarySEwithin(data=mPFC_data_forgot, measurevar = "R_fish", withinvars = c("delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#2C3E50","#5D6D7E","#85929E","#D5D8DC"), labels = c("congruent within", "congruent across", "incongruent within","incongruent across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.08,0.08,0.01),expand = c(0, 0), limits = c(-0.08,0.08))+
  geom_hline(yintercept=0)+
  ggtitle("")+
  ggtitle("mPFC")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")



```


# Same/Sim/Other Correlations 

Forgotten Same/Sim/Other correlations (used for hippocampi)

```{r}
# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("right_hippo_ant", "right_hippo_post","BNA_mPFC2")

# condition: same scene, similar scene, and cross context correlations
grans<-c("simscene", "samescene", "xcon")

# for memories remembered with fine granularity/detail only
grans2<-c("fine")

# subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for(gran2 in grans2){
        for (mask in masks){
          ###### CHANGE PATH FOR YOUR DATA #######
          data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/forgot_",cond,"_corrs_",gran,"_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
          colnames(data)<- c("subj", "trial", "mask", "R")
          data$R_fish<-fisherz(data$R)
          data$condition<-rep(gran, (nrow(data)))
          data$delay<-rep(delay, (nrow(data)))
          data$congruency<-rep(cond, (nrow(data)))
          # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
        data$CB_order<-rep(2, nrow(data))
          # ensure consistent naming of counterbalanced subjects
          for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
         # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          }
        }
          name<-paste(delay,mask,cond,gran,gran2,sep="_")
          assign(name,data) #saves the mean and std under the current masks name
        }
      }
    }
  }
}


#create ant hippo dataset
hippo_right_ant_data_fine_forgot<-rbind(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

# clean up enviro
rm(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

#create post hippo dataset
hippo_right_post_data_fine_forgot<-rbind(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

# clean up enviro
rm(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

```

## Anterior hippocampus 

### Model 
```{r, fig.height=5,fig.width=4.5}
### omnibus 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_ant_data_fine_forgot, na.action=na.omit, control = lmerControl(optimizer ="Nelder_Mead"))

# check model assumptions 
hist(residuals(model)) #should be normal, looks good 
plot(model)#should look fairly uniform and random, looks good 

anova(model)
```

Supplementary Fig. 9 Ant Hippo 
```{r, fig.height=5,fig.width=4.5}
### Break up the plot into all conditions to visualize#### 

eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay:congruency), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

stats<-summarySEwithin(data=hippo_right_ant_data_fine_forgot, measurevar = "R_fish", withinvars = c("congruency","delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("C same scene", "C similar scene", "C other context", "IC same scene", "IC similar scene", "IC other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.05,0.05,0.01), expand = c(0, 0), limits = c(-0.05,0.05))+
  geom_hline(yintercept=0)+
  ggtitle("anterior hippocampus")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```



## Posterior hippocampus 

### Model 
```{r, fig.height=5,fig.width=4.5}
### omnibus 
model<-lmer(R_fish ~ condition*congruency*delay + (1+CB_order|subj), data=hippo_right_post_data_fine_forgot, na.action=na.omit)

## check assumptions 
hist(residuals(model)) #should be normal, looks good 
plot(model)#should look fairly uniform and random, looks good 

anova(model)
```

Supplementary Fig. 9
```{r, fig.height=5,fig.width=4.5}
### Break up the plot into all conditions to visualize#### 

eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay:congruency), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

stats<-summarySEwithin(data=hippo_right_post_data_fine_forgot, measurevar = "R_fish", withinvars = c("congruency","delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("C same scene", "C similar scene", "C other context", "IC same scene", "IC similar scene", "IC other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.05,0.05,0.01), expand = c(0, 0), limits = c(-0.05,0.05))+
  geom_hline(yintercept=0)+
  ggtitle("posterior hippocampus")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```


