---
title: "SCP RSA Object Similarity"
output: html_notebook
---
 
Sam Audrain June 2021
V 0.0.2

This script computes statistical comparisons between patterns for correctly retrieved incongruent trials in mPFC, according to if the objects were related to each other (i.e. kitchen objects/beach objects) or not (arbitrary objects). 

In all cases, objects are incongruent with the background. Congruency only varies between objects. 

# Read in required packages
```{r}
library(nlme)
library(lme4)
library(ggplot2)
library(emmeans)
library(Rmisc)
library(psych)
library(car)
library(lmerTest)
#source("summarySEwithin2.R")
```


# Create dataset for stats comparisons 
- Correlations are fisher transformed into normal distributions for statistical comparison here 

```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("contextO", "arbO", "arbcontextO")

# ROIs
masks<-c("BNA_mPFC2")

#subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")
  
for (delay in delays){
  for (cond in conds){
    for (mask in masks){
      ###### CHANGE PATH FOR YOUR DATA ####### 
      data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/",cond,"_corrs_zscored_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
      colnames(data)<- c("subj", "trial", "mask", "R")
      data$R_fish<-fisherz(data$R)
      data$delay<-rep(delay, (nrow(data)))
      data$cond<-rep(cond, (nrow(data)))
      # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below. 
      data$CB_order<-rep(2, nrow(data))
      # make naming convention the same across delays for counterbalanced subjects 
      for (r in 1:nrow(data)){
        if (data[r,"subj"] == "P201_20181101"){
          data[r,"subj"]<-"P101_20181029"
        } else if (data[r,"subj"] == "S205_20181116"){
          data[r,"subj"]<-"S105_20181113"
        } else if (data[r,"subj"] == "S206_20181122"){
          data[r,"subj"]<-"S106_20181119"
        } else if (data[r,"subj"] == "S207_20181129"){
          data[r,"subj"]<-"S107_20181126"
        } else if (data[r,"subj"] == "S209_20190117"){
          data[r,"subj"]<-"S109_20190114"
        } else if (data[r,"subj"] == "S210_20190123"){
          data[r,"subj"]<-"S110_20190120"
        }
      }
      # insert counterbalancing condition 1 for relevant subjects
      for (r in 1:nrow(data)){
        if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
           data[r,"CB_order"]<- 1
        } 
      }
      name<-paste(delay,mask,cond,sep="_")
      assign(name,data) #saves the mean and std under the current masks name
    }
  }
}


# within context correlation dataset
mPFC_data_arbO<-rbind(short_BNA_mPFC2_arbO, long_BNA_mPFC2_arbO)

mPFC_data_contextO<-rbind(short_BNA_mPFC2_contextO, long_BNA_mPFC2_contextO)

mPFC_data<-rbind(mPFC_data_arbO, mPFC_data_contextO)

# cleanup enviro 
rm(short_BNA_mPFC2_arbcontextO, short_BNA_mPFC2_contextO, short_BNA_mPFC2_arbO, long_BNA_mPFC2_arbcontextO, long_BNA_mPFC2_contextO, long_BNA_mPFC2_arbO)

```


# Model 
```{r, fig.height=5,fig.width=4.5}

# model 
model<-lmer(R_fish ~ cond*delay + (1+CB_order|subj), data=mPFC_data, na.action=na.omit) 

hist(residuals(model))
#check for homogeneity of variance
plot(model)#should look fairly uniform and random. Possible heteroskedasticity? 
data2<-subset(mPFC_data, !is.na(R_fish)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$cond * data2$delay) ## heteroskedastic

# adding weights to allow variance to vary across condiiton and delay 
model<-lme(R_fish ~ cond * delay, random = ~1+CB_order|subj, data=mPFC_data, na.action=na.omit, weights=varIdent(form=~1|cond*delay))
hist(residuals(model)) #check residuals

# model stats 
anova(model)
emmeans(model,list(pairwise ~ delay:cond), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 5076) 

```

Supplementary Fig. 6
```{r, fig.height=5,fig.width=4.5}

## Plot
## use estimated marginal means 
eff_interaction <-emmeans(model, specs = c("delay","cond")) #se is not for within subject data here
eff_interaction_df <- as.data.frame(eff_interaction)
## use within subject se 
stats<-summarySEwithin(data=mPFC_data, measurevar = "R_fish", withinvars = c("cond","delay"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset 
stats$emmean<-eff_interaction_df$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

stats$cond = factor(stats$cond, levels=c("contextO","arbO"))

ggplot(stats, aes(x=delay, y=emmean, fill=cond)) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color="black") + 
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels = c("context-related", "arbitrary"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.08,0.01), expand = c(0, 0), limits = c(0,0.08))+
  geom_hline(yintercept=0)+
  ggtitle("mPFC")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")


```






