---
title: "SCP Connectivity Analysis"
output: html_notebook
---

Sam Audrain November 2020 
V 0.0.1

# Packages and functions
```{r}
library(dplyr)
library(ggplot2)

```

# Read in data
```{r}
data2<-read.csv("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_clean/SCP_connectivity_data.csv")

```

# Correlation tests
```{r}
attach(data2)

# a priori hypothesis testing: Do people with greater post-encoding anterior hippocampal-mPFC coupling have coarser congruent memories 3 days later?
cor.test(post_pre_AH_mPFC, coarse_related_long, alternative = "greater")

# control correlations 
cor.test(post_pre_AH_mPFC, fine_related_long, alternative = "two.sided")
cor.test(post_pre_AH_mPFC, coarse_unrelated_long, alternative = "two.sided")
cor.test(post_pre_AH_mPFC, fine_unrelated_long, alternative = "two.sided")
cor.test(post_pre_AH_mPFC, total_accuracy_long, alternative = "two.sided")
```

# Plot the a priori correlation 
```{r, fig.height=6,fig.width=5.5}

data2 %>%
  ggplot(aes(y = coarse_related_long, x = post_pre_AH_mPFC)) +
  geom_smooth(method = lm, level = 0.95, color = "black") +
  geom_point(size = 5) +
  theme_classic() +
  theme(text = element_text(size = 18), axis.text.x = element_text(size=18), axis.text.y = element_text(size=18), plot.title = element_text(face="bold", hjust=0.5, size=22), legend.position="bottom")+
  scale_shape_manual(values=c(20))+
  guides(shape = FALSE, size = FALSE)+
  labs(y = "coarse congruent retrieval (% of congruent)",
       x = "ant. hipp - mPFC connectivity (post-pre)",
       title = "")


```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
