---
title: "Supplementary Method 8: Pattern similarity within and across contexts in the mPFC restricted to detailed memory trials."
output: html_notebook
---
 
Sam Audrain August 2022
V 2.0

Pattern similarity within and across contexts in the mPFC restricted to detailed memory trials.

# Read in packages
```{r}
library(psych)
library(lme4)
library(nlme)
library(ggplot2)
library(emmeans)
library(Rmisc)
library(car)
library(lmerTest)
library(ggtext)
library(MuMIn)

```

# Create datasets 

Detailed within/across in mPFC 
```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("BNA_mPFC2")

# within context vs across context correlations 
grans<-c("wincon", "xcon")

#subjects in CB1 counterbalancing condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for (mask in masks){
        ###### CHANGE PATH FOR YOUR DATA ####### 
        data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/",cond,"_corrs_",gran,"_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
        colnames(data)<- c("subj", "trial", "mask", "R")
        data$R_fish<-fisherz(data$R) # fisher transformation
        # add in conditions 
        data$condition<-rep(gran, (nrow(data)))
        data$delay<-rep(delay, (nrow(data)))
        data$congruency<-rep(cond, (nrow(data)))
        # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below. 
        data$CB_order<-rep(2, nrow(data))
        # make naming convention the same across delays for counterbalanced subjects 
        for (r in 1:nrow(data)){
          if (data[r,"subj"] == "P201_20181101"){
            data[r,"subj"]<-"P101_20181029"
          } else if (data[r,"subj"] == "S205_20181116"){
            data[r,"subj"]<-"S105_20181113"
          } else if (data[r,"subj"] == "S206_20181122"){
            data[r,"subj"]<-"S106_20181119"
          } else if (data[r,"subj"] == "S207_20181129"){
            data[r,"subj"]<-"S107_20181126"
          } else if (data[r,"subj"] == "S209_20190117"){
            data[r,"subj"]<-"S109_20190114"
          } else if (data[r,"subj"] == "S210_20190123"){
            data[r,"subj"]<-"S110_20190120"
          }
        }
        # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          } 
        }
        name<-paste(delay,mask,cond,gran,sep="_")
        assign(name,data) #saves the mean and std under the current masks name
      }
    }
  }
}



## mPFC 
# within context correlation dataset
mPFC_data_wincon<-rbind(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_UR_wincon)

# within and across context correlation dataset 
mPFC_data<-rbind(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_R_xcon,short_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_UR_xcon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_UR_xcon)

# cleanup enviro 
rm(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_R_xcon,short_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_UR_xcon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_UR_xcon)

```

# Models
## within context correlations according to congruency (congruent/incongruent) x delay (short/long)
```{r, fig.height=5,fig.width=5}

# model 
model<-lme(R_fish ~ congruency*delay, random = ~1+CB_order|subj, data=mPFC_data_wincon, na.action=na.omit, weights=varIdent(form=~1|congruency*delay)) 

# check assumptions 
hist(residuals(model)) # check model residuals 
plot(model)

# model stats
anova(model)
intervals(model, level=0.95, which="fixed")
r.squaredGLMM(model)

# post hocs 
pairwise<-emmeans(model, list(pairwise ~ congruency:delay), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178)
pairwise
confint(pairwise, level=0.95, oldNames=FALSE, method="boot")

```

## condition (within/across context correlations) x delay (short/long) for each congruency (congruent/incongruent)

### congruent 
```{r}

# model 
model<-lme(R_fish ~ condition * delay, random = ~1+CB_order|subj, data=mPFC_data, na.action=na.omit, weights=varIdent(form=~1|condition*delay), subset=congruency=="R")

# check assumptions 
hist(residuals(model))  # check model residuals 

# model stats 
anova(model) ## model stats 
intervals(model, level=0.95, which="fixed")
r.squaredGLMM(model)

```

### incongruent
```{r}

# model 
model<-lme(R_fish ~ condition * delay, random = ~1+CB_order|subj, data=mPFC_data, na.action=na.omit, weights=varIdent(form=~1|condition*delay), subset=congruency=="UR")

# check assumptions
hist(residuals(model))  # check model residuals 

# model stats 
anova(model) ## model stats 
intervals(model, level=0.95, which="fixed")
r.squaredGLMM(model)

```

# Plots

Supplementary Fig.8
```{r, fig.height=5,fig.width=5}

# summarize data 
# prepare for plotting, use lmer model to estimate means since lme won't converge
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=mPFC_data, na.action=na.omit) 

table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay), adjust = "none"))
table<-subset(table, X1 == ".")

stats<-summarySEwithin(data=mPFC_data, measurevar = "R_fish", withinvars = c("delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset, and proper se 
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

# plot 
ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  theme(axis.text=element_text(size=18), axis.title = element_text(size=20), axis.ticks.x=element_blank(), plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom",axis.title.y = ggtext::element_markdown()) +
  labs(fill="") +
  scale_fill_manual(values=c("#2C3E50","#5D6D7E","#85929E","#D5D8DC"), labels = c("congruent within", "congruent across", "incongruent within","incongruent across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.1,0.01),expand = c(0, 0), limits = c(0,0.1))+
  labs(x="", y="similarity (Fisher *z*)", fill="") +
  geom_hline(yintercept=0)+
  ggtitle("mPFC")



```
