---
title: "SCP Behavioural Analysis"
output: html_notebook
---

Sam Audrain June 2021 
V 0.0.2
 
# Packages
```{r}
library(nlme)
library(ggplot2)
library(emmeans)
library(Rmisc)
library(lme4)
library(car)

#library(pbkrtest)
source("summarySEwithin2.R")
```

# Read in and subset the data
```{r}

###### CHANGE PATH FOR YOUR DATA #######
data<-read.csv("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/SCP_behavioural_data.csv")
data$CB_order<-as.factor(data$CB_order)

# subset the data
data_fine<-subset(data, granularity == "fine")
data_coarse<-subset(data, granularity == "coarse")

```


# Investigating accuracy as a function of congruency and delay (collapsed across granularity)

```{r}
# model 
model <-lmer(accuracy_rel ~ delay*congruency + (1|subj), data=data, na.action=na.omit)

## check model assumptions 
hist(residuals(model)) #should be normally distributed 
plot(model)#should look fairly uniform and random. There may be some slight heteroskedasticity here, so test formally with Levene's test
data2<-subset(data, granularity == "coarse" & !is.na(accuracy_rel)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch 
leveneTest(residuals(model) ~ data2$congruency * data2$delay)
leveneTest(residuals(model) ~ data2$congruency)
leveneTest(residuals(model) ~ data2$delay)
## everything looks good, no heteroskedasticity 

### model stats 
anova(model)
emmeans(model, list(pairwise ~ delay:congruency), adjust = "none", lmer.df = "satterthwaite") 

# descriptive stats
stats<-summarySEwithin(data=data, measurevar = "accuracy_rel", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats

```

# Investigating coarse trial accuracy as a function of congruency and delay

```{r}
# model
model<-lmer(accuracy_gran ~ delay*congruency+(1|subj), data=data_coarse, na.action=na.omit)

#check model assumptions 
hist(residuals(model)) ## should be normally distributed, it's looking skewed though
plot(model)#should look fairly uniform and random, looking good 
shapiro.test(residuals(model)) #formally test normality of residuals, they are not normally distributed 

## re-running the model transforming y variable to normalize by taking square root 
model<-lmer(sqrt(accuracy_gran) ~ delay*congruency+(1|subj), data=data_coarse, na.action=na.omit)

## re-check new model assumptions 
hist(residuals(model)) ## should be normally distributed, looking good now 
plot(model)#should look fairly uniform and random, looking ok but test for heteroskedasticity 
shapiro.test(residuals(model)) #residuals are normal now 
## formally testing heteroskedasticity as well
data2<-subset(data, granularity == "coarse" & !is.na(accuracy_gran)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch 
leveneTest(residuals(model) ~ data2$congruency * data2$delay)
leveneTest(residuals(model) ~ data2$congruency)
leveneTest(residuals(model) ~ data2$delay)
## looking good, can proceed 

# Model stats 
anova(model)
emmeans(model, list(pairwise ~ delay:congruency), adjust = "none", lmer.df = "satterthwaite") 

# descriptive stats
stats<-summarySEwithin(data=data_coarse, measurevar = "accuracy_gran", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats

```

## Investigating fine/detailed trial accuracy as a function of congruency and delay

```{r}
# model 
model<-lmer(accuracy_gran ~ delay*congruency + (1+delay|subj), data=data_fine, na.action=na.omit)

# check model assumptions 
hist(residuals(model))
plot(model)#should look fairly uniform and random. It does. 
shapiro.test(residuals(model)) #normal 

# model stats 
anova(model)
emmeans(model, list(pairwise ~ delay:congruency), adjust = "none", lmer.df = "satterthwaite") 

# descriptive stats
stats<-summarySEwithin(data=data_fine, measurevar = "accuracy_gran", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats

```


# Plotting behavioural data
```{r, fig.height=4.5,fig.width=4.5}

########## Get the desired error bars ##########

# fine summary 
stats<-summarySEwithin(data=data_fine, measurevar = "accuracy_gran", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats$upper_se<-NaN
stats$lower_se<-NaN
stats$gran<-rep("fine", length(stats$accuracy_gran))

# coarse summary
stats2<-summarySEwithin(data=data_coarse, measurevar = "accuracy_gran", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats2$upper_se<-NaN
stats2$lower_se<-NaN
stats2$gran<-rep("coarse", length(stats2$accuracy_gran))

#combine the datasets 
stats3<-rbind(stats2,stats)

#get error bars from total related and unrelated 
stats1<-summarySEwithin(data=data, measurevar = "accuracy_rel", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)

#add correct error bars (which represent se collapsed across granularity) to the datset 
# R short 
stats3[7,"upper_se"]<- stats3[7,"accuracy_gran"] + stats3[3,"accuracy_gran"] + stats1[3,"se"]
stats3[7,"lower_se"]<- stats3[7,"accuracy_gran"] + stats3[3,"accuracy_gran"] - stats1[3,"se"]

#UR short
stats3[8,"upper_se"]<- stats3[8,"accuracy_gran"] + stats3[4,"accuracy_gran"] + stats1[4,"se"]
stats3[8,"lower_se"]<- stats3[8,"accuracy_gran"] + stats3[4,"accuracy_gran"] - stats1[4,"se"]

#R long
stats3[5,"upper_se"]<- stats3[5,"accuracy_gran"] + stats3[1,"accuracy_gran"] + stats1[1,"se"]
stats3[5,"lower_se"]<- stats3[5,"accuracy_gran"] + stats3[1,"accuracy_gran"] - stats1[1,"se"]

#UR long
stats3[6,"upper_se"]<- stats3[6,"accuracy_gran"] + stats3[2,"accuracy_gran"] + stats1[2,"se"]
stats3[6,"lower_se"]<- stats3[6,"accuracy_gran"] + stats3[2,"accuracy_gran"] - stats1[2,"se"]


# subset into related and unrelated to plot separately 
stats4<-subset(stats3, congruency == "R")
stats5<-subset(stats3, congruency == "UR") 



########## Plot the data ##########

### congruent plot 
ggplot(stats4[order(stats4$gran, decreasing = T),], aes(x=delay, y=accuracy_gran, fill=factor(gran, levels=c("fine","coarse")))) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "stack", width = 0.6, color="black") + 
  geom_errorbar(width = .0, position = "identity", aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="% correct") +
  theme(axis.title = element_text(size=18), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=16))+
  labs(fill="") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("detailed","coarse"))+ ## for manuscript
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  ggtitle("congruent")+
  theme(plot.title = element_text(size=20, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

### incongruent plot 
ggplot(stats5[order(stats5$gran, decreasing = T),], aes(x=delay, y=accuracy_gran, fill=factor(gran, levels=c("fine","coarse")))) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "stack", width = 0.6,color="black") + 
  geom_errorbar(width = .0, position = "identity", aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="% correct") +
  theme(axis.title = element_text(size=18), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=16))+
  labs(fill="") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("detailed","coarse"))+ ## manuscript 
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  ggtitle("incongruent")+
  theme(plot.title = element_text(size=20, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```

# Proportion Forgotten 
Control analysis to check if PROPORTION of details forotten differs between congruent and incongruent 

proportion forgotten = (short-long)/short

```{r, fig.height=4.5,fig.width=4.5}

# subset the data
data_fine<-subset(data, granularity == "fine")
data_coarse<-subset(data, granularity == "coarse")

# model 
model<-lmer(prop_forgetting ~ granularity*congruency + (1|subj), data=data, na.action=na.omit)
hist(residuals(model)) ## very skewed 
plot(model)#very heteroskedastic 

### residuals not normal, severe negative skew
## I tried transforming the data with inverse, log, etc and just using weights and it didnt help
## skew is coming from some severe datapoints. 

data_subset<-subset(data,include==1) ## have flagged 3 subjects with extreme datapoints in coarse congruent condition, a large increase in coarse congruent memory over time. Removing to deal with heteroskedasticity 

### corrected model, need to use lme so can add weights, because it's still a bit skewed and heteroskedastic even after removing most extreme outliers 
model<-lme(prop_forgetting ~ granularity*congruency, random= ~1|subj, weights=varIdent(form=~1|granularity*congruency), data=data_subset, na.action=na.omit)

## re-check model assumptions 
hist(residuals(model)) #much better 
plot(model)#much better

#model stats 
anova(model)
emmeans(model, list(pairwise ~ granularity*congruency), adjust = "none", lmer.df = "satterthwaite") 

# descriptive stats
stats<-summarySEwithin(data=data_subset, measurevar = "prop_forgetting", withinvars = c("granularity","congruency"), idvar = "subj", na.rm=TRUE)

## PLOT ###
# subset the data
forgetting_fine<-subset(data_subset, delay=="long"& granularity == "fine")
forgetting_coarse<-subset(data_subset, delay=="long"& granularity == "coarse")

## add estiamted marginal mean to the stats dataset
stats$upper_se<-stats$prop_forgetting + stats$se
stats$lower_se<-stats$prop_forgetting - stats$se
stats

ggplot(stats, aes(x=congruency, y=prop_forgetting, fill=granularity)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="proportion forgotten") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#5D6D7E","#85929E","#D5D8DC"), labels = c("coarse", "detailed"))+
  scale_x_discrete(limits=c("R", "UR"), labels=c("R"="congruent", "UR"="incongruent"))+
  scale_y_continuous(breaks = seq(-1.5,1,0.2), expand = c(0, 0), limits = c(-1.5,1))+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")



```




#Plotting correct, DK, and incorrect forgotten trials 

Coarse context (forgot coarse context and therefore the specific scene as well)
```{r, fig.height=4.5,fig.width=4.5}
########## Get the desired error bars ##########

# fine summary DK
stats<-summarySEwithin(data=data_coarse, measurevar = "DK_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats$upper_se<-NaN
stats$lower_se<-NaN
stats$forgot<-rep("DK_perc", length(stats$DK_perc))
colnames(stats)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")

# fine summary incorrect
stats2<-summarySEwithin(data=data_coarse, measurevar = "incorrect_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats2$upper_se<-NaN
stats2$lower_se<-NaN
stats2$forgot<-rep("incorrect_perc", length(stats2$incorrect_perc))
colnames(stats2)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")


#combine the datasets 
stats3<-rbind(stats2,stats)

#get error bars from total related and unrelated 
stats1<-summarySEwithin(data=data, measurevar = "total_forgot_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)

#add correct error bars (which represent se collapsed across granularity) to the datset 
# R short 
stats3[7,"upper_se"]<- stats3[7,"forgot_perc"] + stats3[3,"forgot_perc"] + stats1[3,"se"]
stats3[7,"lower_se"]<- stats3[7,"forgot_perc"] + stats3[3,"forgot_perc"] - stats1[3,"se"]

#UR short
stats3[8,"upper_se"]<- stats3[8,"forgot_perc"] + stats3[4,"forgot_perc"] + stats1[4,"se"]
stats3[8,"lower_se"]<- stats3[8,"forgot_perc"] + stats3[4,"forgot_perc"] - stats1[4,"se"]

#R long
stats3[5,"upper_se"]<- stats3[5,"forgot_perc"] + stats3[1,"forgot_perc"] + stats1[1,"se"]
stats3[5,"lower_se"]<- stats3[5,"forgot_perc"] + stats3[1,"forgot_perc"] - stats1[1,"se"]

#UR long
stats3[6,"upper_se"]<- stats3[6,"forgot_perc"] + stats3[2,"forgot_perc"] + stats1[2,"se"]
stats3[6,"lower_se"]<- stats3[6,"forgot_perc"] + stats3[2,"forgot_perc"] - stats1[2,"se"]


# subset into related and unrelated to plot separately 
stats4<-subset(stats3, congruency == "R")
stats5<-subset(stats3, congruency == "UR")

########## Plot the data ##########

### congruent plot 
ggplot(stats4[order(stats4$forgot, decreasing = T),], aes(x=delay, y=forgot_perc, fill=factor(forgot, levels=c("DK_perc","incorrect_perc")))) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "stack", width = 0.6, color="black") + 
  geom_errorbar(width = .0, position = "identity", aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="% forgotten") + #% of congruent trials at encoding forgotten 
  theme(axis.title = element_text(size=18), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=16))+
  labs(fill="") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("don't know","incorrect"))+ ## for manuscript
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  ggtitle(" ")+
  #ggtitle("congruent context")+
  theme(plot.title = element_text(size=20, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

### incongruent plot 
ggplot(stats5[order(stats5$forgot, decreasing = T),], aes(x=delay, y=forgot_perc, fill=factor(forgot, levels=c("DK_perc","incorrect_perc")))) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "stack", width = 0.6,color="black") + 
  geom_errorbar(width = .0, position = "identity", aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="% forgotten") +
  theme(axis.title = element_text(size=18), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=16))+
  labs(fill="") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("don't know","incorrect"))+ ## manuscript 
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  ggtitle(" ")+
  #ggtitle("incongruent context")+
  theme(plot.title = element_text(size=20, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```



Scenes (answered coarse context correct, got scene incorrect)
```{r, fig.height=4.5,fig.width=4.5}
########## Get the desired error bars ##########

# fine summary DK
stats<-summarySEwithin(data=data_fine, measurevar = "DK_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats$upper_se<-NaN
stats$lower_se<-NaN
stats$forgot<-rep("DK_perc", length(stats$DK_perc))
colnames(stats)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")

# fine summary incorrect
stats2<-summarySEwithin(data=data_fine, measurevar = "incorrect_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)
stats2$upper_se<-NaN
stats2$lower_se<-NaN
stats2$forgot<-rep("incorrect_perc", length(stats2$incorrect_perc))
colnames(stats2)<-c("delay", "congruency", "N", "forgot_perc", "sd", "se", "ci", "upper_se", "lower_se", "forgot")


#combine the datasets 
stats3<-rbind(stats2,stats)

#get error bars from total related and unrelated 
stats1<-summarySEwithin(data=data, measurevar = "total_forgot_perc", withinvars = c("delay","congruency"), idvar = "subj", na.rm=TRUE)

#add correct error bars (which represent se collapsed across granularity) to the datset 
# R short 
stats3[7,"upper_se"]<- stats3[7,"forgot_perc"] + stats3[3,"forgot_perc"] + stats1[3,"se"]
stats3[7,"lower_se"]<- stats3[7,"forgot_perc"] + stats3[3,"forgot_perc"] - stats1[3,"se"]

#UR short
stats3[8,"upper_se"]<- stats3[8,"forgot_perc"] + stats3[4,"forgot_perc"] + stats1[4,"se"]
stats3[8,"lower_se"]<- stats3[8,"forgot_perc"] + stats3[4,"forgot_perc"] - stats1[4,"se"]

#R long
stats3[5,"upper_se"]<- stats3[5,"forgot_perc"] + stats3[1,"forgot_perc"] + stats1[1,"se"]
stats3[5,"lower_se"]<- stats3[5,"forgot_perc"] + stats3[1,"forgot_perc"] - stats1[1,"se"]

#UR long
stats3[6,"upper_se"]<- stats3[6,"forgot_perc"] + stats3[2,"forgot_perc"] + stats1[2,"se"]
stats3[6,"lower_se"]<- stats3[6,"forgot_perc"] + stats3[2,"forgot_perc"] - stats1[2,"se"]


# subset into related and unrelated to plot separately 
stats4<-subset(stats3, congruency == "R")
stats5<-subset(stats3, congruency == "UR")

########## Plot the data ##########

### congruent plot 
ggplot(stats4[order(stats4$forgot, decreasing = T),], aes(x=delay, y=forgot_perc, fill=factor(forgot, levels=c("DK_perc","incorrect_perc")))) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "stack", width = 0.6, color="black") + 
  geom_errorbar(width = .0, position = "identity", aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="% forgotten (context correct)") +
  theme(axis.title = element_text(size=18), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=16))+
  labs(fill="") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("don't know","incorrect"))+ ## for manuscript
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  ggtitle(" ")+
  #ggtitle("congruent scenes")+
  theme(plot.title = element_text(size=20, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

### incongruent plot 
ggplot(stats5[order(stats5$forgot, decreasing = T),], aes(x=delay, y=forgot_perc, fill=factor(forgot, levels=c("DK_perc","incorrect_perc")))) + 
  theme_classic() +
  geom_bar(stat = "identity", position = "stack", width = 0.6,color="black") + 
  geom_errorbar(width = .0, position = "identity", aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="% forgotten (context correct)") +
  theme(axis.title = element_text(size=18), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=16))+
  labs(fill="") +
  scale_fill_manual(values=c("#85929E","#D5D8DC"), labels=c("don't know","incorrect"))+ ## manuscript 
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,100,10),expand = c(0, 0), limits = c(0,100))+
  geom_hline(yintercept=0)+
  ggtitle(" ")+
  # ggtitle("incongruent scenes")+
  theme(plot.title = element_text(size=20, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")
```





