---
title: "Supplementary Analysis 8"
output: html_notebook
---
 
Sam Audrain Feb 2022
V 0.0.3

Looking at patterns in the right posterior hippocampus, regardless of memory quality (i.e. collapsed across coarse/fine). Control analysis. 

# Memory collapsed across caorse/fine in posthippo
```{r}


# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("right_hippo_post")

# condition: same scene, similar scene, and cross context correlations
grans<-c("simscene", "samescene", "xcon")

# for memories remembered with fine granularity/detail only
grans2<-c("fine")

# subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for(gran2 in grans2){
        for (mask in masks){
          ###### CHANGE PATH FOR YOUR DATA ######
          data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/",cond,"_corrs_",gran,"_all_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
          colnames(data)<- c("subj", "trial", "mask", "R", "category")
          data$R_fish<-fisherz(data$R)
          data$condition<-rep(gran, (nrow(data)))
          data$delay<-rep(delay, (nrow(data)))
          data$congruency<-rep(cond, (nrow(data)))
          # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
        data$CB_order<-rep(2, nrow(data))
          # ensure consistent naming of counterbalanced subjects
          for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
         # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          }
        }
          name<-paste(delay,mask,cond,gran,gran2,sep="_")
          assign(name,data) #saves the mean and std under the current masks name
        }
      }
    }
  }
}



#create post hippo dataset
hippo_right_post_data_fine<-rbind(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

# clean up enviro
rm(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)



```

# Right Posterior hippocampus

## Model 
```{r, fig.height=5,fig.width=4.5}
# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=hippo_right_post_data_fine, na.action=na.omit)

# check model assumptions 
hist(residuals(model)) #looks normal 
plot(model)#should look fairly uniform and random. 

# model stats
anova(model)
emmeans(model, list(pairwise ~ delay:congruency), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178) 

```


## Plots

Supplementary Fig. 11
```{r, fig.height=5,fig.width=4.5}
## Plot all conditions, to visualize ##

eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay:congruency), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

stats<-summarySEwithin(data=hippo_right_post_data_fine, measurevar = "R_fish", withinvars = c("congruency","delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("C same scene", "C similar scene", "C other context", "IC same scene", "IC similar scene", "IC other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.1,0.01), expand = c(0, 0), limits = c(0,0.1))+
  geom_hline(yintercept=0)+
  ggtitle("posterior hippocampus")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

