---
title: "SCP RSA Modelling of Context Memory Data"
output: html_notebook
---

Sam Audrain June 2021 
V 0.0.2

The correlations modelled here are context memory correlations. They are trials where participants remember the context (beach/kitchen), regardless of if they remember the specific scene (which beach/kitchen). 

# Read in required packages
```{r}
library(nlme)
library(lme4)
library(lmerTest)
library(ggplot2)
library(emmeans)
library(Rmisc)
library(psych)
library(car)

```


# Create dataset for stats comparisons based on delay and congruency. 
- Correlations are fisher transformed into normal distributions for statistical comparison here 
- organizes within context and across context correlations 

```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("BNA_mPFC2", "right_hippo_ant", "right_hippo_post")

# within context vs across context correlations 
grans<-c("wincon", "xcon")

#subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for (mask in masks){
        ###### CHANGE PATH FOR YOUR DATA ####### 
        data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/",cond,"_corrs_",gran,"_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
        colnames(data)<- c("subj", "trial", "mask", "R")
        data$R_fish<-fisherz(data$R)
        data$condition<-rep(gran, (nrow(data)))
        data$delay<-rep(delay, (nrow(data)))
        data$congruency<-rep(cond, (nrow(data)))
        # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below. 
        data$CB_order<-rep(2, nrow(data))
        # make naming convention the same across delays for counterbalanced subjects 
        for (r in 1:nrow(data)){
          if (data[r,"subj"] == "P201_20181101"){
            data[r,"subj"]<-"P101_20181029"
          } else if (data[r,"subj"] == "S205_20181116"){
            data[r,"subj"]<-"S105_20181113"
          } else if (data[r,"subj"] == "S206_20181122"){
            data[r,"subj"]<-"S106_20181119"
          } else if (data[r,"subj"] == "S207_20181129"){
            data[r,"subj"]<-"S107_20181126"
          } else if (data[r,"subj"] == "S209_20190117"){
            data[r,"subj"]<-"S109_20190114"
          } else if (data[r,"subj"] == "S210_20190123"){
            data[r,"subj"]<-"S110_20190120"
          }
        }
        # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          } 
        }
        name<-paste(delay,mask,cond,gran,sep="_")
        assign(name,data) #saves the mean and std under the current masks name
      }
    }
  }
}



## mPFC 
# within context correlation dataset
mPFC_data_wincon<-rbind(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_UR_wincon)

# within and across context correlation dataset 
mPFC_data<-rbind(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_R_xcon,short_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_UR_xcon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_UR_xcon)

# cleanup enviro 
rm(short_BNA_mPFC2_R_wincon,short_BNA_mPFC2_R_xcon,short_BNA_mPFC2_UR_wincon,short_BNA_mPFC2_UR_xcon,long_BNA_mPFC2_R_wincon,long_BNA_mPFC2_R_xcon, long_BNA_mPFC2_UR_wincon,long_BNA_mPFC2_UR_xcon)

### ant hippo 
# within context correlation dataset
AH_data_wincon<-rbind(short_right_hippo_ant_R_wincon,short_right_hippo_ant_UR_wincon,long_right_hippo_ant_R_wincon,long_right_hippo_ant_UR_wincon)

# within and across context correlation dataset 
AH_data<-rbind(short_right_hippo_ant_R_wincon,short_right_hippo_ant_R_xcon,short_right_hippo_ant_UR_wincon,short_right_hippo_ant_UR_xcon,long_right_hippo_ant_R_wincon,long_right_hippo_ant_R_xcon, long_right_hippo_ant_UR_wincon,long_right_hippo_ant_UR_xcon)

# cleanup enviro 
rm(short_right_hippo_ant_R_wincon,short_right_hippo_ant_R_xcon,short_right_hippo_ant_UR_wincon,short_right_hippo_ant_UR_xcon,long_right_hippo_ant_R_wincon,long_right_hippo_ant_R_xcon, long_right_hippo_ant_UR_wincon,long_right_hippo_ant_UR_xcon)


### post hippo 
# within context correlation dataset
PH_data_wincon<-rbind(short_right_hippo_post_R_wincon,short_right_hippo_post_UR_wincon,long_right_hippo_post_R_wincon,long_right_hippo_post_UR_wincon)

# within and across context correlation dataset 
PH_data<-rbind(short_right_hippo_post_R_wincon,short_right_hippo_post_R_xcon,short_right_hippo_post_UR_wincon,short_right_hippo_post_UR_xcon,long_right_hippo_post_R_wincon,long_right_hippo_post_R_xcon, long_right_hippo_post_UR_wincon,long_right_hippo_post_UR_xcon)

# cleanup enviro 
rm(short_right_hippo_post_R_wincon,short_right_hippo_post_R_xcon,short_right_hippo_post_UR_wincon,short_right_hippo_post_UR_xcon,long_right_hippo_post_R_wincon,long_right_hippo_post_R_xcon, long_right_hippo_post_UR_wincon,long_right_hippo_post_UR_xcon)

```



# mPFC 

## Initial Model fits
```{r, fig.height=5,fig.width=5}

# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=mPFC_data, na.action=na.omit)

# check model assumptions
hist(residuals(model))
plot(model)#should look fairly uniform and random. Possible heteroskedasticity?
# test heteroskedasticity with levene's test
data2<-subset(mPFC_data, !is.na(R_fish)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$congruency * data2$condition *data2$delay) ## heteroskedastic
leveneTest(residuals(model) ~ data2$congruency * data2$condition) ## heteroskedastic
leveneTest(residuals(model) ~ data2$congruency * data2$delay) ## heteroskedastic
leveneTest(residuals(model) ~ data2$delay * data2$condition) ## heteroskedastic

# re-fit the model with lme, using weights to allow variance to vary across each predictor 
## unfortunately, won't converge 
#model<-lme(R_fish ~ condition*congruency*delay, random = ~1|subj, data=mPFC_data, na.action=na.omit, weights=varIdent(form=~1|condition*congruency*delay)) 

## can try robust lmm, which will take care of outliers
#library(robustlmm)
#model.robust<-rlmer(R_fish ~ condition*congruency*delay + (1|subj), data=mPFC_data, na.action=na.omit) ## runs out of memory, can't run 
```

## Model broken down, modelling heteroskedasticity 
*this is what we use in the paper 

### within context correlations according to congruency (congruent/incongruent) x delay (short/long)
```{r, fig.height=5,fig.width=5}
# Break down model into less complex models to test hypotheses of interest, and allow heteroskedasticity. only care about within context correlations here 

# model 
model<-lme(R_fish ~ congruency*delay, random = ~1|subj, data=mPFC_data_wincon, na.action=na.omit, weights=varIdent(form=~1|congruency*delay)) 
hist(residuals(model)) # check model residuals 

# model stats
anova(model)
emmeans(model, list(pairwise ~ congruency:delay), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178)

```

### condition (within/across context correlations) x delay (short/long) for each congruency (congruent/incongruent)
```{r, fig.height=5,fig.width=5}

### congruent ###
# model 
model<-lme(R_fish ~ condition * delay, random = ~1|subj, data=mPFC_data, na.action=na.omit, weights=varIdent(form=~1|condition*delay), subset=congruency=="R")

hist(residuals(model))  # check model residuals 

anova(model) ## model stats 


### incongruent ###
model<-lme(R_fish ~ condition * delay, random = ~1|subj, data=mPFC_data, na.action=na.omit, weights=varIdent(form=~1|condition*delay), subset=congruency=="UR")

hist(residuals(model))  # check model residuals 

anova(model) ## model stats 

```

### Plot 
```{r, fig.height=5,fig.width=5}
### plotting all data 
# prepare for plotting, use lmer model to estimate means since lme won't converge
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=mPFC_data, na.action=na.omit) 

table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay), adjust = "none"))
table<-subset(table, contrast == ".")

stats<-summarySEwithin(data=mPFC_data, measurevar = "R_fish", withinvars = c("delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#2C3E50","#5D6D7E","#85929E","#D5D8DC"), labels = c("congruent within", "congruent across", "incongruent within","incongruent across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  #scale_y_continuous(breaks = seq(-0.01,0.08,0.01),expand = c(0, 0), limits = c(-0.01,0.08))+
  scale_y_continuous(breaks = seq(0,0.08,0.01),expand = c(0, 0), limits = c(0,0.08))+
  geom_hline(yintercept=0)+
  ggtitle("")+
  ggtitle("mPFC")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")




```



# Anterior hippocampmus

## Model
```{r, fig.height=5,fig.width=5}
# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=AH_data, na.action=na.omit) 

# check model assumptions 
hist(residuals(model))
plot(model)
# looks good 

# model stats 
anova(model)
emmeans(model, list(pairwise ~ congruency:delay), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178)
```

## Plot
```{r, fig.height=5,fig.width=5}
# prepare for plotting all effects
table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay), adjust = "none"))
table<-subset(table, contrast == ".")

stats<-summarySEwithin(data=AH_data, measurevar = "R_fish", withinvars = c("delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#7fcdbb","#c7e9b4"), labels = c("congruent within", "congruent across", "incongruent within","incongruent across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.01,0.08,0.01), expand = c(0, 0), limits = c(-0.01,0.08))+
  geom_hline(yintercept=0)+
  ggtitle("anterior hippocampus")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```


# Posterior hippocampus 

## Model
```{r, fig.height=5,fig.width=5}

# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=PH_data, na.action=na.omit) 

# check model assumptions 
hist(residuals(model))
plot(model)
# looks good 

# model stats 
anova(model)
emmeans(model, list(pairwise ~ congruency:delay), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178)
```

## Plot
```{r, fig.height=5,fig.width=5}

# prepare for plotting all effects
table<-as.data.frame(emmeans(model, list(pairwise ~ condition:congruency:delay), adjust = "none"))
table<-subset(table, contrast == ".")

stats<-summarySEwithin(data=PH_data, measurevar = "R_fish", withinvars = c("delay","congruency","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-table$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#7fcdbb","#c7e9b4"), labels = c("congruent within", "congruent across", "incongruent within","incongruent across"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.01,0.08,0.01), expand = c(0, 0), limits = c(-0.01,0.08))+
  geom_hline(yintercept=0)+
  ggtitle("posterior hippocampus")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")


```


