---
title: "SCP RSA Modelling of Scene Memory Data"
output: html_notebook
---
 
Sam Audrain June 2021
V 0.0.2

The correlations modelled here are scene memory correlations. They are trials where participants remember the context (beach/kitchen) and the specific scene (which beach/kitchen). 

# Packages
```{r}
library(nlme)
library(lme4)
library(lmerTest)
library(ggplot2)
library(emmeans)
library(psych)
library(Rmisc)

```


# Create datasets for stats comparisons, on detailed mems 
```{r}

# short = short delay data, long = long delay data
delays<-c("short", "long")

# R = congruent, UR = incongruent
conds<-c("R", "UR")

# ROIs
masks<-c("right_hippo_ant", "right_hippo_post","BNA_mPFC2")

# condition: same scene, similar scene, and cross context correlations
grans<-c("simscene", "samescene", "xcon")

# for memories remembered with fine granularity/detail only
grans2<-c("fine")

# subjects in CB1 condition, i.e. short --> long
CB_SL_subj<-c("P101_20181029","S102_20181101","S103_20181112", "S104_20181113", "S105_20181113", "S106_20181119", "S107_20181126", "S108_20181126", "S109_20190114", "S110_20190120")


for (delay in delays){
  for (cond in conds){
    for (gran in grans){
      for(gran2 in grans2){
        for (mask in masks){
          ###### CHANGE PATH FOR YOUR DATA #######
          data<-read.csv(paste("~/Dropbox/Sam/Schema_Consolidation_Project/R_SCP/SCP_StatsModels_GitHub/RSA_output/",cond,"_corrs_",gran,"_fine_",delay,"_",mask,".csv",sep=""),header = FALSE, sep=" ",stringsAsFactors = FALSE)
          colnames(data)<- c("subj", "trial", "mask", "R")
          data$R_fish<-fisherz(data$R)
          data$condition<-rep(gran, (nrow(data)))
          data$delay<-rep(delay, (nrow(data)))
          data$congruency<-rep(cond, (nrow(data)))
          # putting counterbalancing condition to 2 for everyone since there are more people in this condition. Will swap out those in CB1 below.
        data$CB_order<-rep(2, nrow(data))
          # ensure consistent naming of counterbalanced subjects
          for (r in 1:nrow(data)){
            if (data[r,"subj"] == "P201_20181101"){
              data[r,"subj"]<-"P101_20181029"
            } else if (data[r,"subj"] == "S205_20181116"){
              data[r,"subj"]<-"S105_20181113"
            } else if (data[r,"subj"] == "S206_20181122"){
              data[r,"subj"]<-"S106_20181119"
            } else if (data[r,"subj"] == "S207_20181129"){
              data[r,"subj"]<-"S107_20181126"
            } else if (data[r,"subj"] == "S209_20190117"){
              data[r,"subj"]<-"S109_20190114"
            } else if (data[r,"subj"] == "S210_20190123"){
              data[r,"subj"]<-"S110_20190120"
            }
          }
         # insert counterbalancing condition 1 for relevant subjects
        for (r in 1:nrow(data)){
          if (is.element(data[r, "subj"], CB_SL_subj) == TRUE){
             data[r,"CB_order"]<- 1
          }
        }
          name<-paste(delay,mask,cond,gran,gran2,sep="_")
          assign(name,data) #saves the mean and std under the current masks name
        }
      }
    }
  }
}


#create ant hippo dataset
hippo_right_ant_data_fine<-rbind(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

# clean up enviro
rm(short_right_hippo_ant_R_simscene_fine,short_right_hippo_ant_R_samescene_fine,short_right_hippo_ant_R_xcon_fine, short_right_hippo_ant_UR_simscene_fine,short_right_hippo_ant_UR_samescene_fine,short_right_hippo_ant_UR_xcon_fine,long_right_hippo_ant_R_simscene_fine,long_right_hippo_ant_R_samescene_fine,long_right_hippo_ant_R_xcon_fine, long_right_hippo_ant_UR_simscene_fine,long_right_hippo_ant_UR_samescene_fine,long_right_hippo_ant_UR_xcon_fine)

#create post hippo dataset
hippo_right_post_data_fine<-rbind(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

# clean up enviro
rm(short_right_hippo_post_R_simscene_fine,short_right_hippo_post_R_samescene_fine,short_right_hippo_post_R_xcon_fine, short_right_hippo_post_UR_simscene_fine,short_right_hippo_post_UR_samescene_fine,short_right_hippo_post_UR_xcon_fine,long_right_hippo_post_R_simscene_fine,long_right_hippo_post_R_samescene_fine,long_right_hippo_post_R_xcon_fine, long_right_hippo_post_UR_simscene_fine,long_right_hippo_post_UR_samescene_fine,long_right_hippo_post_UR_xcon_fine)

#create mPFC dataset
BNA_mPFC2_data_fine<-rbind(short_BNA_mPFC2_R_simscene_fine,short_BNA_mPFC2_R_samescene_fine,short_BNA_mPFC2_R_xcon_fine, short_BNA_mPFC2_UR_simscene_fine,short_BNA_mPFC2_UR_samescene_fine,short_BNA_mPFC2_UR_xcon_fine,long_BNA_mPFC2_R_simscene_fine,long_BNA_mPFC2_R_samescene_fine,long_BNA_mPFC2_R_xcon_fine, long_BNA_mPFC2_UR_simscene_fine,long_BNA_mPFC2_UR_samescene_fine,long_BNA_mPFC2_UR_xcon_fine)

# clean up enviro
rm(short_BNA_mPFC2_R_simscene_fine,short_BNA_mPFC2_R_samescene_fine,short_BNA_mPFC2_R_xcon_fine, short_BNA_mPFC2_UR_simscene_fine,short_BNA_mPFC2_UR_samescene_fine,short_BNA_mPFC2_UR_xcon_fine,long_BNA_mPFC2_R_simscene_fine,long_BNA_mPFC2_R_samescene_fine,long_BNA_mPFC2_R_xcon_fine, long_BNA_mPFC2_UR_simscene_fine,long_BNA_mPFC2_UR_samescene_fine,long_BNA_mPFC2_UR_xcon_fine)

```

# Anterior hippocampus

## Model
```{r, fig.height=5,fig.width=4.5}

# model
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=hippo_right_ant_data_fine, na.action=na.omit)

# check model assumptions 
hist(residuals(model)) #should be normal, looks good 
plot(model)#should look fairly uniform and random, looks good 

# model stats 
anova(model)
emmeans(model, list(pairwise ~ condition), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178) 
emmeans(model, list(pairwise ~ condition:delay), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178)
```

## Plots 
```{r, fig.height=5,fig.width=4.5}

# Plot the condition by delay interaction 

#grab the estimated marginal means from the model 
eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

#grab within-subject error bars 
stats<-summarySEwithin(data=hippo_right_ant_data_fine, measurevar = "R_fish", withinvars = c("delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

#plot 
ggplot(stats, aes(x=delay, y=emmean, fill=condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#5D6D7E","#85929E","#D5D8DC"), labels = c("same scene", "similar scene", "other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.08,0.01), expand = c(0, 0), limits = c(0,0.05))+
  geom_hline(yintercept=0)+
  ggtitle("anterior hippocampus
          ")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")



### Break up the plot into all conditions to visualize#### 

eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay:congruency), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

stats<-summarySEwithin(data=hippo_right_ant_data_fine, measurevar = "R_fish", withinvars = c("congruency","delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("C same scene", "C similar scene", "C other context", "IC same scene", "IC similar scene", "IC other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.01,0.1,0.01), expand = c(0, 0), limits = c(-0.01,0.1))+
  geom_hline(yintercept=0)+
  ggtitle("anterior hippocampus")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```

# Posterior hippocampus

## Model 
```{r, fig.height=5,fig.width=4.5}
# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=hippo_right_post_data_fine, na.action=na.omit)

# check model assumptions 
hist(residuals(model)) #looks normal 
plot(model)#should look fairly uniform and random. Possible heteroskedasticity? 
# Levene's test for heteroskedasticity 
data2<-subset(hippo_right_post_data_fine, !is.na(R_fish)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$congruency * data2$condition *data2$delay)
leveneTest(residuals(model) ~ data2$congruency)
leveneTest(residuals(model) ~ data2$delay)
## all good, not heteroskedastic

# model stats
anova(model)
emmeans(model, list(pairwise ~ condition), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178) 

```


## Plots
```{r, fig.height=5,fig.width=4.5}

# Plot condition x delay since those are the main effects 

eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

stats<-summarySEwithin(data=hippo_right_post_data_fine, measurevar = "R_fish", withinvars = c("delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#5D6D7E","#85929E","#D5D8DC"), labels = c("same scene", "similar scene", "other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(0,0.08,0.01), expand = c(0, 0), limits = c(0,0.05))+
  geom_hline(yintercept=0)+
  ggtitle("posterior hippocampus
          ")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")


## Plot all conditions, to visualize ##

eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay:congruency), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

stats<-summarySEwithin(data=hippo_right_post_data_fine, measurevar = "R_fish", withinvars = c("congruency","delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("C same scene", "C similar scene", "C other context", "IC same scene", "IC similar scene", "IC other context"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.01,0.1,0.01), expand = c(0, 0), limits = c(-0.01,0.1))+
  geom_hline(yintercept=0)+
  ggtitle("posterior hippocampus")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")

```



# mPFC

## Original model fits 
```{r, fig.height=5,fig.width=5}
# model 
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=BNA_mPFC2_data_fine, na.action=na.omit)

# check model assumptions 
hist(residuals(model))
#check for homogeneity of variance
plot(model)#should look fairly uniform and random. Possible heteroskedasticity? 
data2<-subset(BNA_mPFC2_data_fine, !is.na(R_fish)) #need to get rid of subjects that were dropped from the model/NA's, otherwise leveneTest will say mismatch
leveneTest(residuals(model) ~ data2$congruency * data2$condition *data2$delay) ## heteroskedastic 
leveneTest(residuals(model) ~ data2$congruency * data2$condition) ## heteroskedastic 
leveneTest(residuals(model) ~ data2$congruency * data2$delay) ## heteroskedastic 

# tried using lme to add weights to take care of it, but it won't converge 
# model<-lme(R_fish ~ condition*congruency*delay, random = ~1|subj, data=BNA_mPFC2_data_fine, na.action=na.omit, weights=varIdent(form=~1|condition*congruency*delay))
```

## Model broken down, modelling heteroskedasticity 

### congruency (congruent/incongruent) x delay (short/long) 
```{r}
#break down model into conditions of interest and weight in lme to allow variance to vary across congruency and delay

# Start with congruency x delay for detailed memories 
model<-lme(R_fish ~ congruency*delay, random = ~1|subj, data=BNA_mPFC2_data_fine, na.action=na.omit, weights=varIdent(form=~1|congruency*delay))

# check model residuals 
hist(residuals(model))

# model stats 
anova(model)
emmeans(model, list(pairwise ~ congruency:delay), adjust = "none", lmer.df = "satterthwaite", lmerTest.limit = 28178)
```

### condtion (same scene/similar scene/across context correlations) x delay (short/long) for each congruency (congruent/incongruent)
```{r}
# Now check condition x delay for each congruency 

### congruent ###
model<-lme(R_fish ~ condition * delay, random = ~1|subj, data=BNA_mPFC2_data_fine, na.action=na.omit, weights=varIdent(form=~1|condition*delay), subset=congruency=="R")
hist(residuals(model)) # check model residuals 
anova(model) # model stats

### incongruent ### 
model<-lme(R_fish ~ condition * delay, random = ~1|subj, data=BNA_mPFC2_data_fine, na.action=na.omit, weights=varIdent(form=~1|condition*delay), subset=congruency=="UR")
hist(residuals(model)) # check model residuals 
anova(model) # model stats

```

### Plots
```{r, fig.height=5,fig.width=5}
# Plot all conditions, to visualize 

## will use the lmer model to estimate the means for the full condition model, since lme doesn't converge 
model<-lmer(R_fish ~ condition*congruency*delay + (1|subj), data=BNA_mPFC2_data_fine, na.action=na.omit)

eff_interaction<-as.data.frame(emmeans(model, list(pairwise ~ condition:delay:congruency), adjust = "none"))
eff_interaction<-subset(eff_interaction, contrast == ".")

stats<-summarySEwithin(data=BNA_mPFC2_data_fine, measurevar = "R_fish", withinvars = c("congruency","delay","condition"), idvar = "subj", na.rm=TRUE)
## add estiamted marginal mean to the stats dataset
stats$emmean<-eff_interaction$emmean
stats$upper_se<-stats$emmean + stats$se
stats$lower_se<-stats$emmean - stats$se
stats

ggplot(stats, aes(x=delay, y=emmean, fill=congruency:condition)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", width = 0.8, color = "black") +
  geom_errorbar(width = .0, position = position_dodge(0.8), aes(ymin=lower_se, ymax=upper_se))+
  labs(x="", y="similarity (Fisher z)") +
  theme(axis.title = element_text(size=20), axis.ticks.x=element_blank()) +
  theme(axis.text=element_text(size=18))+
  labs(fill="") +
  scale_fill_manual(values=c("#253494","#2c7fb8","#41b6c4", "#7fcdbb", "#c7e9b4", "#ffffcc"), labels = c("congruent same", "congruent sim", "congruent other", "incongruent same", "incongruent sim", "incongruent other"))+
  scale_x_discrete(limits=c("short", "long"), labels=c("short", "long"))+
  scale_y_continuous(breaks = seq(-0.01,0.1,0.01), expand = c(0, 0), limits = c(-0.01,0.1))+
  geom_hline(yintercept=0)+
  ggtitle("mPFC")+
  theme(plot.title = element_text(size=22, face="bold", hjust=0.5), legend.text=element_text(size=16), legend.position = "bottom")
```



